### 2017-10-25 analysis/SEMwriteup.Rmd
adding write up a bit

---
title: "Carnegie SEM"
output: pdf_document
---

We are attempting to run an SEM on the Carnegie Classification data to create a new classification system that does not rely on the PCA methodology currently in use. We attempted to run an SEM on the original, raw data, but it was highly right-skewed, so we changed to using ranked data, as the Carnegie Classification currently uses. This data is much more uniformly distributed (for the most part).

```{r, echo=FALSE}
#read in data
setwd("~/Carnegie-SEM/data")
cc2015 <- read.csv("CC2015data.csv",header = TRUE)

########2015################
cc2015.full <- read.csv("CC2015data.csv", header = TRUE, as.is = TRUE)
#updated file
#cc2015.full <- read.csv("Updated2015.csv", header = TRUE)

cc2015 <- cc2015.full[(cc2015.full$BASIC2015>14&cc2015.full$BASIC2015<18),]
cc2015$BASIC2015 <- factor(cc2015$BASIC2015)

#function for ranking the data
minrank <- function(x){rank(x, ties.method = "min")}

#dataset that we want to use
cc2015Ps<-
  na.omit(cc2015[,c("NAME","BASIC2010","BASIC2015","FACNUM","HUM_RSD","OTHER_RSD","SOCSC_RSD","STEM_RSD","PDNFRSTAFF","S.ER.D","NONS.ER.D")])

#calculate the ranked data
cc2015.r <- data.frame(cc2015Ps[,1:3],sapply(cc2015Ps[,-c(1:3)],minrank)) 
cc2015percap <- cc2015Ps[,c("PDNFRSTAFF","S.ER.D","NONS.ER.D")]/cc2015Ps$FACNUM
colnames(cc2015percap) <- c("PDNFRSTAFF_PC", "S.ER.D_PC", "NONS.ER.D_PC")
cc2015percap.r<-data.frame(sapply(cc2015percap,minrank))
cc2015_new <- cbind(cc2015Ps, cc2015percap)
cc2015_r <- cbind(cc2015.r, cc2015percap.r)
```

```{r data_plots, echo=FALSE}
par(mfrow=c(3,4))
hist(cc2015_r$FACNUM, xlab="FACNUM", main="")
hist(cc2015_r$HUM_RSD, xlab="HUM_RSD", main="")
hist(cc2015_r$OTHER_RSD, xlab="OTHER_RSD", main="")
hist(cc2015_r$SOCSC_RSD, xlab="SOCSC_RSD", main="")
hist(cc2015_r$STEM_RSD, xlab="STEM_RSD", main="")
hist(cc2015_r$PDNFRSTAFF, xlab="PDNFRSTAFF", main="")
hist(cc2015_r$S.ER.D, xlab="S.ER.D", main="")
hist(cc2015_r$NONS.ER.D, xlab="NONS.ER.D", main="")
hist(cc2015_r$PDNFRSTAFF_PC, xlab="PNDRFSTAFF_PC", main="")
hist(cc2015_r$S.ER.D_PC, xlab="S.ER.D_PC", main="")
hist(cc2015_r$NONS.ER.D_PC, xlab="NONS.ER.D_PC", main="")
```

We then attempted a regular SEM with the ranked data. This worked, but only with bootstrapped SE estimates and the fit was terrible (RMSEA = 0.9). Upon further exploration of the data, we realized that certain manifest variables in our data were highly correlated.

```{r, echo=FALSE}
cc2015_matrix2 <- as.matrix(cc2015_r[-c(1:3)])
corrmatrix <- Hmisc::rcorr(cc2015_matrix2)
corrplot::corrplot(corrmatrix$r, order="hclust")
```

So, with this new information in hand, we created a new model, aimed at minimizing RMSEA by modeling correlations. This model fit a lot better than the original model (RMSEA = 0.1) but the overall scores we got out were bimodal.

```{r}
model2 <- '
Aggregate=~HUM_RSD+OTHER_RSD+SOCSC_RSD+STEM_RSD+PDNFRSTAFF+S.ER.D+NONS.ER.D
PerCap=~PDNRSTAFF_PC+S.ER.D_PC+NONS.ER.D_PC

Overall=~Aggregate+PerCap

S.ER.D~~S.ER.D_PC
NONS.ER.D~~NONS.ER.D_PC
PDNFRSTAFF~~PDNRSTAFF_PC
PDNFRSTAFF~~S.ER.D
HUM_RSD~~SOCSC_RSD
S.ER.D~~STEM_RSD
PDNRSTAFF_PC~~S.ER.D_PC
NONS.ER.D~~HUM_RSD
NONS.ER.D~~SOCSC_RSD
'

lavaan_sem_r_cov <- lavaan::sem(model2, data=cc2015_r, std.lv=TRUE, orthogonal=FALSE, se="robust.huber.white")
semPlot::semPaths(lavaan_sem_r_cov)
#lavaan::summary(lavaan_sem_r_cov, fit.measures=TRUE)
CCScores_r_cov <- as.data.frame(lavaan::predict(lavaan_sem_r_cov))
density(CCScores_r_cov$Overall)
range_scores <- max(CCScores_r_cov$Overall) - min(CCScores_r_cov$Overall)
CCScores_r_cov$rate_2015 <- ifelse(CCScores_r_cov$Overall < min(CCScores_r_cov$Overall)+((1/3)*range_scores), 'A', ifelse(CCScores_r_cov$Overall > max(CCScores_r_cov$Overall)-((1/3)*range_scores), 'C', 'B'))
CC_table <- as.data.frame(cbind(cc2015_new$NAME, cc2015_new$BASIC2015, CCScores_r_cov$rate_2015))
colnames(CC_table) <- c("name", "basic2015", "rate2015")
table(cc2015_new$BASIC2015, CC_table$rate2015)
```

Recalling that our original data did not follow a modal distribution, the results seemed strange, and the contingency table showed that we only seemed to able to match up with the highest rating group. With that haing seemingly failed in producing three groups, we switched to Bayesian SEM models.

#Paul's Bayesian Stuff

### 2017-10-27 analysis/SEMwriteup.Rmd
ch.chh.chhh...changes

@@
 title: "Carnegie SEM"
+author: "Sarah McKnight and Paul Harmon"
 output: pdf_document
@@
 
+#Introduction:
 We are attempting to run an SEM on the Carnegie Classification data to create a new classification system that does not rely on the PCA methodology currently in use.
+The Carnegie Classifications are currently based on two data-driven PCAs, meaning that loadings can change from year to year.
+We hope to create a stable model that better allows for comparisons on a single dimension.
+This was done using Structural Equation Modeling (SEM).
+
 We attempted to run an SEM on the original, raw data, but it was highly right-skewed, so we changed to using ranked data, as the Carnegie Classification currently uses.
-This data is much more uniformly distributed (for the most part).
+Each of the metrics are ranked based on the minimum method for ties.
+These data are much more uniformly distributed than the original data, which were highly skewed in the positive direction.
+These data included very large values for outlier institutions such as MIT and Harvard, but most of the schools were clustered at smaller values.
 
@@
 #Paul's Bayesian Stuff
+An alternative to the traditional SEM model is the Bayesian SEM, which allows for prior distributions to be put on the latent variables.
+
+In a traditional SEM model, the manifors
+
+These models can be fit using the package "blavaan" (Merkle and Rosseel 2016); however, it is a beta package that is still being tested for validity and stability.
+
+## Testing with Linear Regression
+To better understand the mechanics of the R package Blavaan, we tried fitting a simple regression model to a dataset with which were already familiar.
+We were able to match the estimates with a linear model using lm(), which is expected.
+The choice of priors was Normal.
+
+## A First Model
+
+## Changing Priors
+
+## Sensitivity to Priors
+
+##Bayesian SEM - Some Conclusions
+
+#Comparing the SEM model to the Carnegie Classifications
+The SEM model and the PCA-based Carnegie model were both used to make plots of aggregate and per-capita traits associated with each institution.
+Neither plot produces multiple well-separated groups; however, the PCA-based method is slightly more well-separated.
+
+```{r}
+###lets see if we can calculate distances with schools
+Score_dist <- as.data.frame(cbind(CCScores_r_cov_scale, PC_pred_scale))
+rownames(Score_dist) <- cc2015_new$NAME
+
+#recreates the PC-based plot
+ggplot(Score_dist) + geom_point(aes(x = PC_ag_pred, y = -PC_percap_pred, color = cc2015_new$BASIC2015)) + ggtitle("Carnegie Classification PC Plot")
+
+ggplot(Score_dist) + geom_point(aes(x = Aggregate, y = PerCap, color = CCScores_r_cov$rate_2015))
+
+#calculate distances 
+get_Distance <- function(x1,x2,y1,y2){
+
+ #calculates the euclidean distance between the points  
+  dist <- sqrt((x2 - x1)^2 + (y2 - y1)^2)
+ #returns distances
+  return(dist)
+}
+
+Score_dist$Distance <- c()
+
+for (j in 1:nrow(Score_dist)){
+  Score_dist$Distance[j] <- get_Distance(x1 = Score_dist[j,"Aggregate"],x2 = Score_dist[j,"PC_ag_pred"],y1 = Score_dist[j,"PerCap"],y2 = Score_dist[j,"PC_percap_pred"])
+}
+
+#Let's look at distances
+sorted <- Score_dist[order(Score_dist$Distance),]
+head(sorted,10)
+tail(sorted,10)
+
+summary(Score_dist$Distance)
+
+#show biggest movers on Carnegie Classifications Plot
+ggplot(Score_dist) + geom_point(aes(x = PC_ag_pred, y = PC_percap_pred, color = as.factor(round(Distance)))) + ggtitle("Biggest Movers")
+
+```

### 2017-10-27 analysis/SEMwriteup.Rmd
some more changes to the writeup

@@
 ```{r, echo=FALSE}
+par(mfrow = c(1,1))
 cc2015_matrix2 <- as.matrix(cc2015_r[-c(1:3)])
@@
 Aggregate=~HUM_RSD+OTHER_RSD+SOCSC_RSD+STEM_RSD+PDNFRSTAFF+S.ER.D+NONS.ER.D
-PerCap=~PDNRSTAFF_PC+S.ER.D_PC+NONS.ER.D_PC
+PerCap=~PDNFRSTAFF_PC+S.ER.D_PC+NONS.ER.D_PC
 
@@
 NONS.ER.D~~NONS.ER.D_PC
-PDNFRSTAFF~~PDNRSTAFF_PC
+PDNFRSTAFF~~PDNFRSTAFF_PC
 PDNFRSTAFF~~S.ER.D
@@
 S.ER.D~~STEM_RSD
-PDNRSTAFF_PC~~S.ER.D_PC
+PDNFRSTAFF_PC~~S.ER.D_PC
 NONS.ER.D~~HUM_RSD
@@
 ```{r}
+#Generates PCA scores for comparison
+PC_ag <- prcomp(cc2015.r[,-c(1,2,3,4)], scale = TRUE)
+PC_percap <- prcomp(cc2015percap.r, scale = TRUE)
+
+PC_ag_pred <- predict(PC_ag)[,1]
+PC_percap_pred <- predict(PC_percap)[,1]
+
+PC_pred_scale <- apply(as.data.frame(cbind(PC_ag_pred,PC_percap_pred)),2,scale)
+
+#predicts the scores
+CCScores_r_cov <- as.data.frame(lavaan::predict(lavaan_sem_r_cov))
+CCScores_r_cov_scale <- apply(CCScores_r_cov[,c(1,2)], 2, scale)
+
 ###lets see if we can calculate distances with schools
@@
 ggplot(Score_dist) + geom_point(aes(x = Aggregate, y = PerCap, color = CCScores_r_cov$rate_2015))
+```
 
+#Which Schools Move the Most?
+The plot below shows which schools move the most relative to their location on the Carnegie classifications.
+These movements are not systematic; while most of the schools that move the most are near the center, they are not all occurning in one classification level.
+
+```{r,distances, fig.align = 'center'}
 #calculate distances 
@@
   dist <- sqrt((x2 - x1)^2 + (y2 - y1)^2)
+ distx <- x2 - x1
+ disty <- y2 - y1
   #returns distances
-  return(dist)
+  return(list( dist = dist, distx = distx, disty = disty ))
 }
@@
 for (j in 1:nrow(Score_dist)){
-  Score_dist$Distance[j] <- get_Distance(x1 = Score_dist[j,"Aggregate"],x2 = Score_dist[j,"PC_ag_pred"],y1 = Score_dist[j,"PerCap"],y2 = Score_dist[j,"PC_percap_pred"])
+  Score_dist$Distance[j] <- get_Distance(x1 = Score_dist[j,"Aggregate"],x2 = Score_dist[j,"PC_ag_pred"],y1 = Score_dist[j,"PerCap"],y2 = -Score_dist[j,"PC_percap_pred"])$dist
+
   }
@@
 #show biggest movers on Carnegie Classifications Plot
-ggplot(Score_dist) + geom_point(aes(x = PC_ag_pred, y = PC_percap_pred, color = as.factor(round(Distance)))) + ggtitle("Biggest Movers")
+ggplot(Score_dist) + geom_point(aes(x = PC_ag_pred, y = -PC_percap_pred, color = as.factor(floor(Distance)))) + ggtitle("Biggest Movers")
 
 ```
+
+#Additional Ways to Visualize These Models
+There are two ways that we can visualize these plots.
+One uses GGplot to create path diagrams in a ggplot-based framework.
+These are similar to the SemPlot package but may allow for a bit more post processing of the plots.
+The unfortunate aspect of these plots is that they have to be put together piece by piece - there's no function that directly interfaces with lavaan to get the solution.
+```{r}
+#add code to produce a path diagram here
+```
+
+An alternative way to look at these models would be to uses the Onyx package, which interfaces with the lavaan code but allows for you to make changes to the path diagrams in a separate window.
+These are not great for this kind of context but they are useful for creating pretty-looking path diagrams.
+Onyx has to be installed from GitHub to work, but other than that it interfaces nicely with lavaan objects.
+```{r}
+library(onyxR)
+onyx(lavaan_sem_r_cov)
+onyx(lavaan_sem_b)
+onyx(lavaan_sem_r)
+```

### 2017-11-01 SEM_presentation.Rmd
presentation

---
title: "Carnegie SEM"
author: "Paul Harmon and Sarah McKnight"
date: "November 1, 2017"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The Carnegie Classifications

- Based on PCA
- Two Scales: Aggregate (x-axis) and Per-Capita (y-axis)

![The 2015 Classifications]()

## How are Scores Calculated?
The Carnegie Classifications are based on ranked data (because some schools are vastly larger on certain metrics than the rest). The ranked data are partitioned into two datasets and a PCA is generated on the both datasets. The first PC score is then used as an index for each trait.

## Aggregate and Per-Capita Indices

The classifications are calculated based on two indices of institutional output. The first is based on a weighted average of the number of PhDs awarded by the institution; the second is based on a per-capita measurement of research expenditures and research staff. 
__Aggregate Index:__
$$Ag.Index_{i}  = HumanitiesPhD_{i} + StemPhD_{i} + SocialSciencePhD_{i} + OtherPhD_{i}  + StemExpenditures_{i} + NonStemExpenditures_{i} + ResearchStaff_{i} $$ 
__Per Capita Index:__ 
$$PC.Index_{i} = \frac{ResearchStaff_{i} + StemExpenditures_{i} + NonStemExpenditures_{i}}{FacultySize_{i}} $$

## PCA Plot - Arbitrary Boundaries

From here, the methodology of the Carnegie Classifications is to produce a plot of the two correlated indices. Lines are arbitrarily drawn to create three partitions of the space. The following plot is produced.

![The 2015 Classifications with lines](https://github.com/paulharmongj/Writing-Project/Carnegie Classifications/Presentation_for_writing_maybe_files/figure-beamer/unstandardized scores-1.pdf)

## Problems with PCA
Many of the decisions made in this process are data driven and are outside the control of researchers:

+ Aggregate and Per-Capita Indices were constructed so that they are correlated, 
+ Attributes of the PCA change from year to year, meaning important policy drivers in one year might not be important in the next year (Social Science PhDs) 
+ Data are rarely grouped into three neat clusters, and lines are arbitrarily drawn

__Because of this, we wanted to try fitting a Structural Equation Model to create an index to compete with the Carnegie Classifications__

## Structural Equation Models
__GoaL__: Model two latent traits, one for the aggreagate scale and the other for the per-capita scale, and then use those to generate a "super-latent" single trait.

We could then separate institutions into groups via univariate model-based clustering or something as simple as breaking the single variable into several groups.

##SEM Model

##Path Diagram

##Questions

### 2017-11-02 Laura_pres.Rmd
adding presentations

---
title: "Presentation For Laura"
author: "Paul Harmon and Sarah McKnight"
date: "November 2, 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
#read in data
setwd("~/Carnegie-SEM/data")
cc2015 <- read.csv("CC2015data.csv",header = TRUE)

########2015################
cc2015.full <- read.csv("CC2015data.csv", header = TRUE, as.is = TRUE)
#updated file
#cc2015.full <- read.csv("Updated2015.csv", header = TRUE)

cc2015 <- cc2015.full[(cc2015.full$BASIC2015>14&cc2015.full$BASIC2015<18),]
cc2015$BASIC2015 <- factor(cc2015$BASIC2015)

#function for ranking the data
minrank <- function(x){rank(x, ties.method = "min")}

#dataset that we want to use
cc2015Ps<-
  na.omit(cc2015[,c("NAME","BASIC2010","BASIC2015","FACNUM","HUM_RSD","OTHER_RSD","SOCSC_RSD","STEM_RSD","PDNFRSTAFF","S.ER.D","NONS.ER.D")])

#calculate the ranked data
cc2015.r <- data.frame(cc2015Ps[,1:3],sapply(cc2015Ps[,-c(1:3)],minrank))

cc2015percap <- cc2015Ps[,c("PDNFRSTAFF","S.ER.D","NONS.ER.D")]/cc2015Ps$FACNUM
colnames(cc2015percap) <- c("PDNRSTAFF_PC", "S.ER.D_PC", "NONS.ER.D_PC")
cc2015percap.r<-data.frame(sapply(cc2015percap,minrank))

#sem using raw data
cc2015_new <- cbind(cc2015Ps, cc2015percap)

cc2015_r <- cbind(cc2015.r, cc2015percap.r)

```

## The Carnegie Classifications

- Based on PCA on correlation matrix of ranked institutional data
- Two Scales: Aggregate (x-axis) and Per-Capita (y-axis)
_ Three categories of PhD-granting institutions: R1 to R3

## Carnegie in 2015
![The 2015 Classifications](figures/2015classifications.png)

## How are Scores Calculated?
The Carnegie Classifications are based on ranked data (because some schools are vastly larger on certain metrics than the rest). The ranked data are partitioned into two datasets and a PCA is generated on the both datasets. The first PC score is then used as an index for each trait.

## Aggregate and Per-Capita Indices

The classifications are calculated based on two indices of institutional output. The first is based on a weighted average of the number of PhDs awarded by the institution; the second is based on a per-capita measurement of research expenditures and research staff. 
__Aggregate Index:__
$$Ag.Index_{i}  = HumanitiesPhD_{i} + StemPhD_{i} + SocialSciencePhD_{i}$$
$$+ OtherPhD_{i}  + StemExpenditures_{i} + NonStemExpenditures_{i} + ResearchStaff_{i} $$ 
__Per Capita Index:__ 
$$PC.Index_{i} = \frac{ResearchStaff_{i} + StemExpenditures_{i} + NonStemExpenditures_{i}}{FacultySize_{i}} $$

## PCA Plot - Arbitrary Boundaries

From here, the methodology of the Carnegie Classifications is to produce a plot of the two correlated indices. Lines are arbitrarily drawn to create three partitions of the space. The following plot is produced.

## Problems with PCA
Many of the decisions made in this process are data driven and are outside the control of researchers:

+ Aggregate and Per-Capita Indices were constructed so that they are correlated, but how correlated they are can change from year to year
+ Attributes of the PCAs themselves change from year to year, meaning important policy drivers in one year might not be important in the next year (Social Science PhDs) 
+ This can affect policy decisions made based on the classifications
+ Data are rarely grouped into three neat clusters, and lines are arbitrarily drawn
+ Both PCAs throw out roughly 30 percent of the variation in underlying variables

![PCA: Carnegie Classifications](figures/2015classifications.png)
__Because of this, we wanted to try fitting a Structural Equation Model to create an index to compete with the Carnegie Classifications__

## Structural Equation Models
__GoaL__: Model two latent traits, one for the __aggreagate scale__ and the other for the __per-capita scale__, and then use those to generate a "super-latent" single trait.

We could then separate institutions into groups via univariate model-based clustering or something as simple as breaking the single variable into several groups.

## Problems Solved by the SEM
The SEM is constructed a priori because we set the latent variables and correlation structure beforehand. This leads to a solution that is less succeptible to change when the data are updated.

+ We don't have an arbitray curve slicing up groups of schools - it's either cut based on a model-based clustering algorithm or sliced into proportional groups.

##SEM Model
Output from SEM Model is below. The RMSEA was initially close to 0.9 but after modeling covariances, we were able to get it down to 0.1. This model had the lowest AIC value of any we fit and the tests for the manifest variables and correlations were found to be _statistically significant_. 
```{r lavaan_code, include = TRUE}
model2 <- '
Aggregate=~HUM_RSD+OTHER_RSD+SOCSC_RSD+STEM_RSD+PDNFRSTAFF+S.ER.D+NONS.ER.D
PerCap=~PDNRSTAFF_PC+S.ER.D_PC+NONS.ER.D_PC

Overall=~Aggregate+PerCap

S.ER.D~~S.ER.D_PC
NONS.ER.D~~NONS.ER.D_PC
PDNFRSTAFF~~PDNRSTAFF_PC
PDNFRSTAFF~~S.ER.D
HUM_RSD~~SOCSC_RSD
S.ER.D~~STEM_RSD
PDNRSTAFF_PC~~S.ER.D_PC
NONS.ER.D~~HUM_RSD
NONS.ER.D~~SOCSC_RSD
'

#Generates the SEM
lavaan_sem_r_cov <- lavaan::sem(model2, data=cc2015_r, std.lv=TRUE, orthogonal=FALSE, se="robust.huber.white")
lavaan::summary(lavaan_sem_r_cov, fit.measures=TRUE)

CCScores_r_cov <- as.data.frame(lavaan::predict(lavaan_sem_r_cov))
CCScores_r_cov_scale <- apply(CCScores_r_cov[,c(1,2)], 2, scale)
range_scores <- max(CCScores_r_cov$Overall) - min(CCScores_r_cov$Overall)
CCScores_r_cov$rate_2015 <- ifelse(CCScores_r_cov$Overall < min(CCScores_r_cov$Overall)+((1/3)*range_scores), 'A', ifelse(CCScores_r_cov$Overall > max(CCScores_r_cov$Overall)-((1/3)*range_scores), 'C', 'B'))
CC_table <- as.data.frame(cbind(cc2015_new$NAME, cc2015_new$BASIC2015, CCScores_r_cov$rate_2015))
colnames(CC_table) <- c("name", "basic2015", "rate2015")
table(cc2015_new$BASIC2015, CC_table$rate2015)
```

![Plot of the SEM latent traits](figures/semplot1.png)

##Path Diagram
```{r}
library(semPlot)
par(mar = c(4,2,3,2))
semPaths(lavaan_sem_r_cov, col = "skyblue",intercepts = FALSE, XKCD = TRUE)
text(-1,1.2,"Path Diagram", font = 2, cex = 2)
```

## Densities of Our Scores

```{r, message = FALSE, warning = FALSE}
CCScores_r_cov_predicted <- as.data.frame(lavaan::predict(lavaan_sem_r_cov))
plot(density(CCScores_r_cov_predicted$Overall))
```

## PCA vs. SEM

```{r}
#Generates PCA scores for comparison
PC_ag <- prcomp(cc2015.r[,-c(1,2,3,4)], scale = TRUE)
PC_percap <- prcomp(cc2015percap.r, scale = TRUE)

PC_ag_pred <- predict(PC_ag)[,1]
PC_percap_pred <- predict(PC_percap)[,1]

PC_pred_scale <- apply(as.data.frame(cbind(PC_ag_pred,PC_percap_pred)),2,scale)

Score_dist <- as.data.frame(cbind(CCScores_r_cov_scale, PC_pred_scale))
rownames(Score_dist) <- cc2015_new$NAME

#recreates the PC-based plot
ggplot(Score_dist) + geom_point(aes(x = PC_ag_pred, y = -PC_percap_pred, color = cc2015_new$BASIC2015)) + ggtitle("Carnegie Classification PC Plot")

ggplot(Score_dist) + geom_point(aes(x = Aggregate, y = PerCap, color = CCScores_r_cov$rate_2015))

#calculate distances 
get_Distance <- function(x1,x2,y1,y2){

 #calculates the euclidean distance between the points  
  dist <- sqrt((x2 - x1)^2 + (y2 - y1)^2)
 distx <- x2 - x1
 disty <- y2 - y1
  #returns distances
  return(list( dist = dist, distx = distx, disty = disty ))
}

Score_dist$Distance <- c()

for (j in 1:nrow(Score_dist)){
  Score_dist$Distance[j] <- get_Distance(x1 = Score_dist[j,"Aggregate"],x2 = Score_dist[j,"PC_ag_pred"],y1 = Score_dist[j,"PerCap"],y2 = -Score_dist[j,"PC_percap_pred"])$dist

  }

#Let's look at distances
sorted <- Score_dist[order(Score_dist$Distance),]
head(sorted,10)
tail(sorted,10)

summary(Score_dist$Distance)

#show biggest movers on Carnegie Classifications Plot
ggplot(Score_dist) + geom_point(aes(x = PC_ag_pred, y = -PC_percap_pred, color = as.factor(floor(Distance)))) + ggtitle("Biggest Movers")

```

##Questions For Laura

+ What is the official term for "super  latent trait"?
+  Could we improve the fit by doing something other than just modeling covariances?
+ Comparing scores from PCA to SEM - is this reasonable?

##Thanks!

### 2017-11-15 Laura_pres.Rmd
adding some more stuff

@@
 - Two Scales: Aggregate (x-axis) and Per-Capita (y-axis)
-_ Three categories of PhD-granting institutions: R1 to R3
+- Three categories of PhD-granting institutions: R1 to R3
 
@@
 ## Densities of Our Scores
-
+Distribution was bimodal - schools were grouped into two groups
 ```{r, message = FALSE, warning = FALSE}
@@
 plot(density(CCScores_r_cov_predicted$Overall))
+library(beanplot)
+beanplot(CCScores_r_cov_predicted$Overall, col = c("blue",'orange'), method = "jitter")
+title("SEM Classifications")
 ```

### 2017-11-15 CarnegieSEM_paul.R

@@ -216,7 +216,7 @@ HUM=~HUM_RSD + OTHER_RSD + SOCSC_RSD + NONS.ER.D + FACNUM
 Overall=~STEM+HUM
 
 
-
+#covariances - maybe omit?
 NONS.ER.D ~~ HUM_RSD
 NONS.ER.D ~~ SOCSC_RSD
 

### 2017-11-15 analysis/paul_script.R

@@ -1,4 +1,7 @@
 #read in data
+
+
+
 setwd("C:/Users/paulh/Downloads")
 cc2015 <- read.csv("CC2015data.csv",header = TRUE)
 
@@ -120,14 +123,29 @@ blavInspect(bSEM, "psrf") #check Potential Scale Reduction Factor
 
 #lavaan.survey
 
-#
-svy.ob <- svydesign(fpc = ~1, data = ranked_dat, ids = rep(1,length(ranked_dat[,1])))
+#svy.ob <- svydesign(fpc = ~1, data = ranked_dat, ids = rep(1,length(ranked_dat[,1])))
 lavaan.survey(model.carnegie.ranked, survey.design = svy.ob)
 
 
+##Per meeting November 2, I looked at a couple of other SEM MODELS 
 
+model.carnegie.ranked <- '
+#measurement model
+ag_overall =~ S.ER.D + NONS.ER.D + STEM_RSD + SOCSC_RSD + OTHER_RSD + HUM_RSD + PDNFRSTAFF + FACNUM
 
+#Correlations
+S.ER.D ~~ STEM_RSD 
+S.ER.D ~~ PDNFRSTAFF
+NONS.ER.D ~~ HUM_RSD
+NONS.ER.D ~~ SOCSC_RSD
+SOCSC_RSD ~~ HUM_RSD
+STAFFPC ~~ SERDPC
 
+#with per-capita stuff
+S.ER.D ~~ SERDPC
+NONS.ER.D ~~ NONSERDPC
+PDNFRSTAFF ~~ STAFFPC
+'
 
 
 

### 2018-04-05 Laura_pres.Rmd
Moving over from GitLab repo, all files

@@
 - Two Scales: Aggregate (x-axis) and Per-Capita (y-axis)
-- Three categories of PhD-granting institutions: R1 to R3
+-u Three categories of PhD-granting institutions: R1 to R3
 

### 2018-04-05 SEMstuff_laura.Rmd
Moving over from GitLab repo, all files

---
title: "SEM Code"
author: "Paul"
date: "March 6, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Correlation Plot
We used the correlation plot below to inform the two latent factors that we are using.

```{r}
setwd("~/Carnegie-SEM/data")
cc2015 <- read.csv("CC2015data.csv",header = TRUE)

########2015################
cc2015.full <- read.csv("CC2015data.csv", header = TRUE, as.is = TRUE)
#updated file
#cc2015.full <- read.csv("Updated2015.csv", header = TRUE)

cc2015 <- cc2015.full[(cc2015.full$BASIC2015>14&cc2015.full$BASIC2015<18),]
cc2015$BASIC2015 <- factor(cc2015$BASIC2015)

#function for ranking the data
minrank <- function(x){rank(x, ties.method = "min")}

#dataset that we want to use
cc2015Ps<-
  na.omit(cc2015[,c("NAME","BASIC2010","BASIC2015","FACNUM","HUM_RSD",
                    "OTHER_RSD","SOCSC_RSD","STEM_RSD","PDNFRSTAFF","S.ER.D","NONS.ER.D")])

#calculate the ranked data
cc2015.r <- data.frame(cc2015Ps[,1:3],sapply(cc2015Ps[,-c(1:3)],minrank))

cc2015percap <- cc2015Ps[,c("PDNFRSTAFF","S.ER.D","NONS.ER.D")]/cc2015Ps$FACNUM
colnames(cc2015percap) <- c("PDNRSTAFF_PC", "S.ER.D_PC", "NONS.ER.D_PC")
cc2015percap.r<-data.frame(sapply(cc2015percap,minrank))
cc2015_r <- cbind(cc2015.r, cc2015percap.r)

cc2015_matrix2 <- as.matrix(cc2015_r[-c(1:3)])
corrmatrix <- Hmisc::rcorr(cc2015_matrix2)
corrplot::corrplot(corrmatrix$r, order="hclust")
```

##SEM Code:

The SEM fit below on the STEM and Non-STEM latent factors is given with the following code.

```{r}
model4 <- '
HUMANITIES=~HUM_RSD+OTHER_RSD+SOCSC_RSD+NONS.ER.D+FACNUM
STEM=~STEM_RSD+PDNFRSTAFF+S.ER.D+FACNUM
Aggregate=~HUMANITIES+STEM'

lavaan_sem_new <- lavaan::sem(model4, data=cc2015_r, std.lv=TRUE,
                              orthogonal=FALSE, se="robust.huber.white")
lavaan::summary(lavaan_sem_new, standardized=TRUE, fit.measures=TRUE)
CCScores <- as.data.frame(lavaan::predict(lavaan_sem_new))
rownames(CCScores) <- cc2015Ps$NAME

```

### 2018-04-05 analysis/SEMwriteup.Rmd
Moving over from GitLab repo, all files

@@
 
-In a traditional SEM model, the manifors
-
 These models can be fit using the package "blavaan" (Merkle and Rosseel 2016); however, it is a beta package that is still being tested for validity and stability.
@@
 ## A First Model
+The first model considered was the bayesian SEM with no additional changes made to the code.
+The estimates were quite different from those calculated in the original SEM.
+We looked into the priors and saw that some of them were pretty highly informative.
+```{r}
+require(blavaan)
+bsem_norm <- blavaan::bsem(model2, data=cc2015_r, cp='srs', std.lev=TRUE, convergence='auto', dp=dpriors())
+summary(bsem_norm)
+```
 
 ## Changing Priors
+The highly informative priors should have shrunk the estimators a little too much, so we decided to try some normal priors with large variance terms (in order to not be so informative).
+Since the latent variables are assumed in a frequentist setting to be multivariate normals, we assumed that normal priors with large variances would be uninformative and thus reasonable.
+However, using them gave us even more shrunk estimates compared to the frequentist SEM.
+```{r}
+bNORM <- blavaan::bsem(model2, data=cc2015_r, cp='srs', std.lv=TRUE, convergence='auto', dp=dpriors(lambda="dnorm(0,10000)"))
+summary(bNORM) #lambda
+```
 
 ## Sensitivity to Priors
+As of now, the sensitivity of the prior choice is a problem. We want fairly stable estimates and the Blavaan method is  not giving us something particularly useful.
 
-##Bayesian SEM - Some Conclusions
+Moreover, Blavaan kicks the estimation of posteriors out to JAGS, and occasionally convergence issues have been a problem.
+It may be better to think about coding out a Bayesian version of SEM by ourselves rather than fitting the SEM using a package.
 
@@
 
-ggplot(Score_dist) + geom_point(aes(x = Aggregate, y = PerCap, color = CCScores_r_cov$rate_2015))
+ggplot(Score_dist) + geom_point(aes(x = Aggregate, y = PerCap, color = cc2015_new$BASIC2015))
 ```

### 2018-04-05 for_laura.Rmd
Moving over from GitLab repo, all files

--- 2018-04-05 SEMstuff_laura.Rmd
@@
 ---
-title: "SEM Code"
-author: "Paul"
-date: "March 6, 2018"
+title: "For Laura"
+author: "Paul Harmon and Sarah McKnight"
+date: "December 11, 2017"
 output: pdf_document
@@
 
-##Correlation Plot
-We used the correlation plot below to inform the two latent factors that we are using.
+We generated a new SEM model for the Carnegie Data in order to get things to run efficiently. The code for generating the model and reading in the dataset is given below.
 
 ```{r}
+#read in data
 setwd("~/Carnegie-SEM/data")
@@
 
-##SEM Code:
+Based on the inability of the previous model to generate a positive-definite variance covariance matrix, we looked back at the model and determined that things are too highly correlated to get things to work.
+Rather than modeling the Aggregate and Per-Capita traits from the same set of variables, we decided to look at STEM vs.
+Non-STEM differences.
+This allowed us to have two correlated factors, but they did not depend on the same variables so we were able to get results that looked reasonable.
 
-The SEM fit below on the STEM and Non-STEM latent factors is given with the following code.
-
+The model fit is below: 
 ```{r}
@@
 ```
+
+The model would look like the following, in a path diagram:
+
+```{r}
+library(semPlot)
+semPaths(lavaan_sem_new)
+```
+
+Finally, we can generate a plot of the factors plotted against each other: 
+```{r}
+library(ggplot2)
+CCScores_r_cov_new <- as.data.frame(lavaan::predict(lavaan_sem_new))
+names(CCScores_r_cov_new)
+    #creates a plot and colors by Carnegie Classification Colors  
+  ggplot(CCScores_r_cov_new) + geom_point(aes(x = STEM, y = HUMANITIES), color = "gray30", symbol = "gray30")+ 
+   ggtitle("Predicted vs Actual Classifications") + theme_bw() + coord_fixed(ratio = 1)
+```

### 2018-04-05 SEM_app/SEM_app.R

@@ -30,9 +30,7 @@ ui <- fluidPage(
     sidebarPanel(
       
       selectInput(inputId = "school", "School", choices = names, selected = NULL, multiple = FALSE,
-                  selectize = TRUE, width = NULL, size = NULL)
-      
-      , 
+                  selectize = TRUE, width = NULL, size = NULL), 
       
       hr(),
       
@@ -87,6 +85,7 @@ ui <- fluidPage(
     # Show a plot of the generated distribution
     mainPanel(
       plotOutput("classPlot"),
+      tableOutput("swag")
           )
   )
 )
@@ -199,7 +198,15 @@ COLOR <- rep(1,nrow(new_dat)); COLOR[a] <- 2
 
   
   #render some test text
-  output$swag <- renderText("Hello World!")
+  output$swag <- renderTable({
+  
+    inst_name <- new_school()
+    a <- which(as.character(cc2015Ps$NAME) == as.character(inst_name))
+    
+    new_table <- cc2015Ps[a,]
+    
+    new_table
+      }) 
     
 }
 

### 2018-04-05 analysis/paul_script.R

@@ -6,7 +6,7 @@ setwd("C:/Users/paulh/Downloads")
 cc2015 <- read.csv("CC2015data.csv",header = TRUE)
 
 ########2015################
-cc2015.full <- read.csv("CC2015data.csv", header = TRUE, as.is = TRUE)
+cc2015.full <- read.csv("data/CC2015data.csv", header = TRUE, as.is = TRUE)
 #updated file
 #cc2015.full <- read.csv("Updated2015.csv", header = TRUE)
 

### 2018-04-05 jjkl/app.R

@@ -1,0 +1,52 @@
+#
+# This is a Shiny web application. You can run the application by clicking
+# the 'Run App' button above.
+#
+# Find out more about building applications with Shiny here:
+#
+#    http://shiny.rstudio.com/
+#
+
+library(shiny)
+
+# Define UI for application that draws a histogram
+ui <- fluidPage(
+   
+   # Application title
+   titlePanel("Old Faithful Geyser Data"),
+   
+   # Sidebar with a slider input for number of bins 
+   sidebarLayout(
+      sidebarPanel(
+         sliderInput("bins",
+                     "Number of bins:",
+                     min = 1,
+                     max = 50,
+                     value = 30)
+      ),
+      
+      # Show a plot of the generated distribution
+      mainPanel(
+         plotOutput("distPlot")
+      )
+   )
+)
+
+# Define server logic required to draw a histogram
+server <- function(input, output) {
+   
+  output$college <- reactive({s
+    })
+   output$distPlot <- renderPlot({
+      # generate bins based on input$bins from ui.R
+      x    <- faithful[, 2] 
+      bins <- seq(min(x), max(x), length.out = input$bins + 1)
+      
+      # draw the histogram with the specified number of bins
+      hist(x, breaks = bins, col = 'darkgray', border = 'white')
+   })
+}
+
+# Run the application 
+shinyApp(ui = ui, server = server)
+

### 2018-04-05 April_Presentation.Rmd
presentation

---
title: "Untitled"
author: "Paul Harmon"
date: "April 2, 2018"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Institutional Classifications
Systems for identifying like institutions, ranking universities, and delineating similar groups of peer-schools are used by students, faculty and administrators alike. They include:

+ The Carnegie Classifications for Higher Education
+ The US News World Ranking
+ Times Higher Ed

However, each one is subjective, and no perfect classifier exists. However, administrators use these to inform policy decisions (Montana State University, Idaho University), so it is useful to know how they work.

## The Carnegie Classifications

The Carnegie Classifications delineate doctoral-granting institutions into three groups: 
+ R1: Very High Research
+ R2: High Research
+ R3: Moderate Research

Previously, they had been updated every five years. However, that has changed to a three year cycle in the future. Data are collected in a snapshot from IPEDS and other sources to be used in each update.

## The Carnegie Methodology

+ Rank Institutions
+ Index Creation: PCA of aggregate and per-capita variables
+ Plot the Indices (per-capita vs aggregate)
+ Create groups (via line-drawing)

## Principal Components Analysis 
Principal Componenents Analysis is a method for dimension reduction that takes a set of p predictor variables and decomposes it into k principal components that explain the most variation in the underlying variables.

![picture]()

## Problems with Carnegie System
The process used by the Carnegie Classifications illustrates several problems:
+ Snapshot Data
+ 
+ 
+

## Structural Equation Modeling

Structural Equation Models (SEM)

## The Carnegie Method using SEMs

## STEM and Non-STEM Factors
A more intuitive method would be to consider two latent factors:

+ STEM productivity 
+ Non-STEM productivity

Variables loaded onto these factors are not as likely to be correlated.

## Determining Group Membership
The SEM model returns a single factor score for each university. These can be used as inputs to a

## Group Membership

## Future Work

## Conclusions and

### 2018-04-05 analysis/SEM_CleanCode.R
changes to correlation plot and code

@@ -1,11 +1,11 @@
 
 
 #read in data
-setwd("~/Carnegie-SEM/data")
-cc2015 <- read.csv("CC2015data.csv",header = TRUE)
+#setwd("~/Carnegie-SEM/data")
+cc2015 <- read.csv("data/CC2015data.csv",header = TRUE)
 
 ########2015################
-cc2015.full <- read.csv("CC2015data.csv", header = TRUE, as.is = TRUE)
+cc2015.full <- read.csv("data/CC2015data.csv", header = TRUE, as.is = TRUE)
 #updated file
 #cc2015.full <- read.csv("Updated2015.csv", header = TRUE)
 
@@ -25,13 +25,26 @@ cc2015Ps<-
 cc2015.r <- data.frame(cc2015Ps[,1:3],sapply(cc2015Ps[,-c(1:3)],minrank)) 
 
 cc2015percap <- cc2015Ps[,c("PDNFRSTAFF","S.ER.D","NONS.ER.D")]/cc2015Ps$FACNUM
+
+
 colnames(cc2015percap) <- c("PDNRSTAFF_PC", "S.ER.D_PC", "NONS.ER.D_PC")
+#for Corrplot, nothing else
+
+
 cc2015percap.r<-data.frame(sapply(cc2015percap,minrank))
 cc2015_r <- cbind(cc2015.r, cc2015percap.r)
+names(cc2015_r) <- c("Name","2010 Basic","2015 Basic","Faculty Size", "Hum PhD",
+                     "Other PhD","Soc. Sci PhD", "STEM PhD","Res. Staff", "STEM Exp", 
+                     "NS Exp", "Res. Staff PC", "STEM Exp PC  ", "NS Exp PC")
 
 cc2015_matrix2 <- as.matrix(cc2015_r[-c(1:3)])
 corrmatrix <- Hmisc::rcorr(cc2015_matrix2)
-corrplot::corrplot(corrmatrix$r, order="hclust")
+
+par(mar = c(1,.8,.8,2))
+corrplot::corrplot(corrmatrix$r, order="hclust", type = "upper")
+text(-4,3, 'Correlation Plot', font = 2)
+text(-4,2,'of Manifest Variables', font = 2)
+rect(-7,1.3,-1,3.5)
 
 model4 <- '
 HUMANITIES=~HUM_RSD+OTHER_RSD+SOCSC_RSD+NONS.ER.D+FACNUM

### 2018-04-06 analysis/SEM_CleanCode.R
mas chanegeados have been made-o... yeah, I took five years of spanish

@@ -33,6 +33,7 @@ colnames(cc2015percap) <- c("PDNRSTAFF_PC", "S.ER.D_PC", "NONS.ER.D_PC")
 
 cc2015percap.r<-data.frame(sapply(cc2015percap,minrank))
 cc2015_r <- cbind(cc2015.r, cc2015percap.r)
+#RUN THIS FOR CORRPLOT: (commented out otherwise)
 names(cc2015_r) <- c("Name","2010 Basic","2015 Basic","Faculty Size", "Hum PhD",
                      "Other PhD","Soc. Sci PhD", "STEM PhD","Res. Staff", "STEM Exp", 
                      "NS Exp", "Res. Staff PC", "STEM Exp PC  ", "NS Exp PC")
@@ -41,7 +42,7 @@ cc2015_matrix2 <- as.matrix(cc2015_r[-c(1:3)])
 corrmatrix <- Hmisc::rcorr(cc2015_matrix2)
 
 par(mar = c(1,.8,.8,2))
-corrplot::corrplot(corrmatrix$r, order="hclust", type = "upper")
+corrplot::corrplot(corrmatrix$r, order="hclust", type = "upper", method = 'number')
 text(-4,3, 'Correlation Plot', font = 2)
 text(-4,2,'of Manifest Variables', font = 2)
 rect(-7,1.3,-1,3.5)
@@ -51,11 +52,23 @@ HUMANITIES=~HUM_RSD+OTHER_RSD+SOCSC_RSD+NONS.ER.D+FACNUM
 STEM=~STEM_RSD+PDNFRSTAFF+S.ER.D+FACNUM
 Aggregate=~HUMANITIES+STEM'
 
+model4 <- '
+non-STEM = ~ Hum PhD + Other PhD + Soc. Sci PhD + 
+STEM
+'
+
+
 lavaan_sem_new <- lavaan::sem(model4, data=cc2015_r, std.lv=TRUE,
                               orthogonal=FALSE, se="robust.huber.white")
 lavaan::summary(lavaan_sem_new, standardized=TRUE, fit.measures=TRUE)
 CCScores <- as.data.frame(lavaan::predict(lavaan_sem_new))
 rownames(CCScores) <- cc2015Ps$NAME
+
+#path diagram
+
+source('https://raw.githubusercontent.com/brandmaier/onyxR/master/tools/install.R')
+library(onyxR)
+onyx(lavaan_sem_new)
 
 library(beanplot)
[…]

### 2018-04-06 analysis/SEM_CleanCode.R
inspect standardized factor loadings added

@@ -64,6 +64,9 @@ lavaan::summary(lavaan_sem_new, standardized=TRUE, fit.measures=TRUE)
 CCScores <- as.data.frame(lavaan::predict(lavaan_sem_new))
 rownames(CCScores) <- cc2015Ps$NAME
 
+#checks the standardized factor loadings
+inspect(lavaan_sem_new, what = 'std')$lambda
+
 #path diagram
 
 source('https://raw.githubusercontent.com/brandmaier/onyxR/master/tools/install.R')

### 2018-04-11 April_Presentation.Rmd
adding a ton of stuff to the repo

@@
 ---
-title: "Untitled"
-author: "Paul Harmon"
+title: "An Alternative to the Carnegie Classifications:"
+subtitle: "Using Structural Equation Models to Identify Similar Doctoral Institutions"
+author: |
+  | Paul Harmon
+  | with Sarah McKnight, Laura Hildreth, Ian Godwin and Mark Greenwood
+  | Montana State University
+
 date: "April 2, 2018"
-output: beamer_presentation
+output:
+  beamer_presentation:
+    theme: "boxes"
+    colortheme: "crane"
+    fonttheme: "structuresmallcapsserif"
+    fig_caption: false
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
+library(ggplot2)
+```
+
+```{r, include = FALSE}
+
+#read in data
+setwd("C:/Users/paulh/Documents/Carnegie-SEM/Carnegie_SEM")
+cc2015 <- read.csv("data/CC2015data.csv",header = TRUE)
+
+########2015################
+cc2015.full <- read.csv("data/CC2015data.csv", header = TRUE, as.is = TRUE)
+#updated file
+#cc2015.full <- read.csv("Updated2015.csv", header = TRUE)
+
+cc2015 <- cc2015.full[(cc2015.full$BASIC2015>14&cc2015.full$BASIC2015<18),]
+cc2015$BASIC2015 <- factor(cc2015$BASIC2015)
+
+#function for ranking the data
+minrank <- function(x){rank(x, ties.method = "min")}
+
+#dataset that we want to use
+cc2015Ps<-
+  na.omit(cc2015[,c("NAME","BASIC2010","BASIC2015","FACNUM","HUM_RSD",
+                    "OTHER_RSD","SOCSC_RSD","STEM_RSD","PDNFRSTAFF","S.ER.D","NONS.ER.D")])
+
+#calculate the ranked data
+cc2015.r <- data.frame(cc2015Ps[,1:3],sapply(cc2015Ps[,-c(1:3)],minrank))
+
+cc2015percap <- cc2015Ps[,c("PDNFRSTAFF","S.ER.D","NONS.ER.D")]/cc2015Ps$FACNUM
+
+colnames(cc2015percap) <- c("PDNRSTAFF_PC", "S.ER.D_PC", "NONS.ER.D_PC")
+#for Corrplot, nothing else
+
+cc2015percap.r<-data.frame(sapply(cc2015percap,minrank))
+cc2015_r <- cbind(cc2015.r, cc2015percap.r)
+
+model4 <- '
+HUMANITIES=~HUM_RSD+OTHER_RSD+SOCSC_RSD+NONS.ER.D+FACNUM
+STEM=~STEM_RSD+PDNFRSTAFF+S.ER.D+FACNUM
+Aggregate=~HUMANITIES+STEM'
+
+library(lavaan)
+lavaan_sem_new <- lavaan::sem(model4, data=cc2015_r, std.lv=TRUE,
+                              orthogonal=FALSE, se="robust.huber.white")
+lavaan::summary(lavaan_sem_new, standardized=TRUE, fit.measures=TRUE)
+CCScores <- as.data.frame(lavaan::predict(lavaan_sem_new))
+rownames(CCScores) <- cc2015Ps$NAME
+
+#checks the standardized factor loadings
+inspect(lavaan_sem_new, what = 'std')$lambda
+
+library(mclust)
+mcres<-Mclust(CCScores$Aggregate)
+summary(mcres)
+
+Classifications <- as.data.frame(mcres[14:15])
+rownames(Classifications) <- cc2015Ps$NAME
+
+table(mcres$classification, cc2015Ps$BASIC2015) ## pretty good!!
+
+#Or more directly:
+dens<-densityMclust(CCScores$Aggregate)
+summary(dens)
+par(mfrow=c(1,2))
+plot(dens,what="diagnostic")
+
+#Or clustering the STEM and HUMANITIES scores (bivariate version)
+mcres2<-Mclust(CCScores[,1:2])
+
 ```
@@
 The Carnegie Classifications delineate doctoral-granting institutions into three groups:
+
 + R1: Very High Research
@@
 
+## The Carnegie Classifications
+![](figures/2015classifications.png)
+
+## What Data are used?
+Data used in the Carnegie Classifications are based on a snapshot from the Integrated Postsecondary Education Data System (IPEDS). The variables used in the classifications are:
+
++ **STEM expenditures** (in thousands of dollars)
++ **Non-STEM expenditures** (in thousands of dollars)
++ **Nontenurable Research Staff size**
++ STEM PhD Counts
++ Humanities PhD Counts
++ Social Science PhD Counts
++ Other PhD Counts
+
++ *Tenured/Tenure Track Faculty Headcount*
+
+**Per-Capita**: The 3 variables in bold are used in per-capita variables by dividing by Faculty Headcount.
+
 ## The Carnegie Methodology
 
-+ Rank Institutions
-+ Index Creation: PCA of aggregate and per-capita variables
-+ Plot the Indices (per-capita vs aggregate)
-+ Create groups (via line-drawing)
+The Carnegie Classifications are built on the following methodology:
 
-## Principal Components Analysis 
-Principal Componenents Analysis is a method for dimension reduction that takes a set of p predictor variables and decomposes it into k principal components that explain the most variation in the underlying variables.
++ **Rank** Institutions on 7 aggregate variables and 3 per-capita variables
++ **Index Creation**: PCA of aggregate and per-capita variables
++ **Plot the Indices**:  (per-capita vs aggregate)
++ **Create groups**:  (via line-drawing)
 
-![picture]()
+## Principal Component Analysis 
+Principal Componenent Analysis is a method for dimension reduction that takes a set of p predictor variables and decomposes it into k principal components that explain the most variation in the underlying variables.
+
++ Principal Components are weighted averages of the observed variables
++ In the Carnegie Classifications, they create the aggregate index by taking the first principal component from a PCA of 7 aggregate variables
++ The per-capita index is the first principal component from a PCA of 3 per-capita variables
 
@@
 The process used by the Carnegie Classifications illustrates several problems:
-+ Snapshot Data
-+ 
-+ 
-+
+
++ **Based on Snapshot Data**: Data are based on a single snapshot rather than averages during the five-year period.  
++ **Changing Loadings**: Loadings can change yearly based on variability in the data.
+This has the potential to change which variables are most important in determining the aggregate and per-capita indices.
++ **Dependence on Correlation**:  
++ **Group Determination**: The group determination is completely subjective. Lines are drawn after visual inspection of the plot.
+
+This causes problems for schools that try to direct policy based on these classifications because the most important variables can be different from release to release based on variability in the data.
 
@@
 
-Structural Equation Models (SEM)
+Structural Equation Models (SEM) are used to model simultaneous equations, the use of latent or unobserved variables, and variables to be measured with error.
+
++ **Latent Variable Model**: Measures unobserved variables. 
++ **Measurement Model**: Relates the latent variables we are interested in to the manifest that we actually observe.
 
@@
 
-## STEM and Non-STEM Factors
+We can think of the Carnegie Classifications in a latent modeling framework using this path diagram:
+
+![Carnegie Model](analysis/carnegiepng.png)
+
+##Problems with the Carnegie Method for SEM:
+The variables used to measure the aggregate and per-capita latent variables are the same (with a slight per-capita transformation).
+The SEM cannot handle this level of correlation in the two latent factors; it **does not converge** and thus paramaters cannot be estimated.
+
+## STEM and Non-STEM Factors: An Alternative
 A more intuitive method would be to consider two latent factors:
@@
 
+## STEM and Non-STEM Manifest Correlations
+
+![](corrplot_numbers.png)
+
+```{r, fig.cap = 'Correlations of Manifest Variables', fig.width =4 , fig.height = 2, eval = FALSE}
+#RUN THIS FOR CORRPLOT: (commented out otherwise)
+cc2015_r_new <- cc2015_r
+names(cc2015_r_new) <- c("Name","2010 Basic","2015 Basic","Faculty Size", "Hum PhD",
+                     "Other PhD","Soc. Sci PhD", "STEM PhD","Res. Staff", "STEM Exp", 
+                     "NS Exp", "Res. Staff PC", "STEM Exp PC  ", "NS Exp PC")
+
+cc2015_matrix2 <- as.matrix(cc2015_r_new[-c(1:3)])
+corrmatrix <- Hmisc::rcorr(cc2015_matrix2)
+
+par(mar = c(1,.8,.8,2))
+corrplot::corrplot(corrmatrix$r, order="hclust", type = "upper", method = 'number')
+text(-4,3, 'Correlation Plot', font = 2)
+text(-4,2,'of Manifest Variables', font = 2)
+rect(-7,1.3,-1,3.5)
+
+```
+
+##Proposed Model: STEM and Non-STEM
+![Carnegie Model](analysis/onyx_final.png)
+
 ## Determining Group Membership
-The SEM model returns a single factor score for each university. These can be used as inputs to a
+The SEM model returns a single factor-of-factor score for each university.
+These can be used as inputs to a clustering algorithm to determine both the optimal number of clusters and the optimal cluster membership.
 
-## Group Membership
+__Potential Problems__:
+
++ Optimal Number of Clusters may be too large/small: We can fix this to a reasonable number if necessary (results here are fixed at 3). 
++ There are many different clustering methods to use (hierarchical clustering, mixture-model based methods, etc.).
+
+## Group Membership with Mixture Model:
+
+Using a mixture model, we can objectively define clusters. Additionally, we can illustrate uncertainty in classification for schools near the boundary.
+
+```{r plot_classifications, fig.align = 'center',fig.height = 6, fig.width = 6}
+Classifications <- mcres$classification
+#creates a plot and colors by Carnegie Classification Colors
+
+#adds the bobcat to plot
+library(png)
+library(grid)
+img <- readPNG("msu_logo.png")
+stf <- readPNG("stanford_trans.png")
+g <- rasterGrob(img, interpolate=FALSE)
+stan <- rasterGrob(stf, interpolate = FALSE)
+
+a <- which(rownames(CCScores)=="Montana State University")
+b <- which(rownames(CCScores) == 'Stanford University')
+
+MSU_x <- CCScores$STEM[a]
+MSU_y <- CCScores$HUMANITIES[a]
+stan_x <- CCScores$STEM[b]
+stan_y <- CCScores$HUMANITIES[b]
+    ggplot(CCScores) + geom_point(aes(x = STEM, y = HUMANITIES, color = factor(Classifications)))+ 
+      ggtitle("Predicted vs Actual Classifications") + theme_bw() + coord_fixed(ratio = 1)+
+      theme_classic() + 
+      #theme(legend.position="right", legend.box = "vertical") + 
+      labs(color = "Classification") + 
+       annotation_custom(g, xmin = MSU_x-.25 , xmax=MSU_x+.35, ymin= MSU_y -.3, ymax=MSU_y + .25) + annotation_custom(stan, xmin = stan_x-.25 , xmax=stan_x+.35, ymin= stan_y -.3, ymax=stan_y + .25)
+
+```
+
+## Uncertainty in Classifications
+The Carnegie Classifications treat each classification as a fixed value, without accounting for the uncertainty inherent in the process.
+
++ Variability in underlying data
++ Uncertainty in PCA
++ Uncertainty in Mixture Modeling
+
+Our method can be used to visualize differences in the data.
+
+## Uncertainty Plots
+```{r, fig.width = 8, fig.height = 5, fig.align = 'center'}
+
+library(mclust)
+mcres<-Mclust(CCScores$Aggregate)
+#summary(mcres)
+par(mfrow=c(1,2))
+par(mar = c(1,1,1.2,1))
+#plot(mcres,what="BIC")
+plot(mcres,what="classification", col = c("red","green",'blue'))
+legend('topleft',fill = c('red','green','blue'),legend = c("1",'2','3'))
+plot(mcres,what="uncertainty", col = c("red",'green','blue') )
+legend('topleft',fill = c('red','green','blue'),legend = c("1",'2','3'))
+#plot(mcres,what="density")
+```
+
+## Shiny Applications: 
+We developed shiny applications to assess sensitivity of both the Carnegie Classifications and the proposed SEM-Classifications for any institution of your choosing.
+
++ Sliders allow for user to change counts of PhDs, Staff/Faculty size, Expenditures
++ User can select any Doctoral-granting institution
++ The SEM application uses a fixed number of three clusters
+
+These applications can be found at: paulharmon.shiny.io/SEM-class
+
+## Shiny Applications:
+
+![Screenshot of the Application](analysis/app_screenshot_small.png)
+
+## Conclusions
+
+The SEM-based model allows for several benefits compared to the Carnegie Classifications:
+
++ Latent variables do not have to be orthogonal like PCA-based indices
++ Latent variable modeling makes more sense than dimension-reduction (especially since we only have 7 variables)
++ Single-factor scores allow for comparison on a single dimension rather than using two scores.
 
@@
 
-## Conclusions and
+Future work will focus on determining an optimal clustering strategy.
+The Carnegie Classifications themselves are changing, so if they change the variables that are used, we will investigate development of either a new latent trait or sensitivity of additional manifest variables to measure the STEM and non-STEM latent traits.
+
+## Questions:
+\centering
+Thank you!

### 2018-04-11 Latex/ims-sample.tex
adding a ton of stuff to the repo

\documentclass[aoas,preprint]{imsart}

\RequirePackage[OT1]{fontenc}
\RequirePackage{amsthm,amsmath}
\RequirePackage[numbers]{natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

% settings
%\pubyear{2005}
%\volume{0}
%\issue{0}
%\firstpage{1}
%\lastpage{8}
\arxiv{arXiv:0000.0000}

\startlocaldefs
\numberwithin{equation}{section}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\endlocaldefs

\begin{document}

\begin{frontmatter}
\title{An Alternative to the Carnegie Classifications: Using Structural Equation Models to Identify Similar Doctoral Institutions\thanksref{T1}}
\runtitle{A Sample Document}
\thankstext{T1}{Footnote to the title with the ``thankstext'' command.}

\begin{aug}
\author{\snm{Paul Harmon}\thanksref{t1,t2,m1}\ead[label=e1]{paulharmongj@gmail.com}},
\author{\fnms{Sarah McKnight} \thanksref{t3,m1,m2}\ead[label=e2]{second@somewhere.com}}
\author{\fnms{Laura Hildreth} \thanksref{t3,m1,m2}\ead[label=e2]{second@somewhere.com}}
\author{\fnms{Ian Godwin} \thanksref{t3,m1,m2}\ead[label=e2]{second@somewhere.com}}

\and
\author{\fnms{Mark Greenwood} \snm{Author}\thanksref{t1,m2}
\ead[label=e3]{greenwood@montana.edu}

\thankstext{t1}{Some comment}
\thankstext{t2}{First supporter of the project}
\thankstext{t3}{Second supporter of the project}
\runauthor{F. Author et al.}

\affiliation{Montana State University\thanksmark{m1}}

\address{Address of the First and Second authors\\
Usually a few lines long\\
\printead{e1}\\
\phantom{E-mail:\ }\printead*{e2}}

\address{Address of the Third author\\
Usually a few lines long\\
Usually a few lines long\\
\printead{e3}\\
\printead{u1}}
\end{aug}

\begin{abstract}
The abstract should summarize the contents of the paper.
It should be clear, descriptive, self-explanatory and not longer
than 200 words. It should also be suitable for publication in
abstracting services. Please avoid using math formulas as much as possible.

This is a sample input file.  Comparing it with the output it
generates can show you how to produce a simple document of
your own.
\end{abstract}

\begin{keyword}[class=MSC]
\kwd[Primary ]{60K35}
\kwd{60K35}
\kwd[; secondary ]{60K35}
\end{keyword}

\begin{keyword}
\kwd{sample}
\kwd{\LaTeXe}
\end{keyword}

\end{frontmatter}

\section{Ordinary text}

The ends  of words and sentences are marked
  by   spaces. It  doesn't matter how many
spaces    you type; one is as good as 100.  The
end of   a line counts as a space.

One   or more   blank lines denote the  end
of  a paragraph.

Since any number of consecutive spaces are treated like a single
one, the formatting of the input file makes no difference to
      \TeX,         % The \TeX command generates the TeX logo.
but it makes a difference to you.
When you use
      \LaTeX,       % The \LaTeX command generates the LaTeX logo.
making your input file as easy to read as possible
will be a great help as you write your document and when you
change it.  This sample file shows how you can add comments to
your own input file.

Because printing is different from typewriting, there are a
number of things that you have to do differently when preparing
an input file than if you were just typing the document directly.
Quotation marks like
       ``this''
have to be handled specially, as do quotes within quotes:
       ``\,`this'                  % \, separates the double and single quote.
    is what I just
    wrote, not  `that.'\,''

Dashes come in three sizes: a hyphen, %an intra-word dash, 
a medium dash for number ranges like
       1--2,
and a punctuation dash in place of a comma, semicolon, colon or parentheses
       ---like
this.

A sentence-ending space should be larger than the space between words
within a sentence.  You sometimes have to type special commands in
conjunction with punctuation characters to get this right, as in the
following sentence.
       Gnats, gnus, etc.\    % `\ ' makes an inter-word space.
       all begin with G\@.   % \@ marks end-of-sentence punctuation.
You should check the spaces after periods when reading your output to
make sure you haven't forgotten any special cases.
Generating an ellipsis
       \ldots\    % `\ ' needed because TeX ignores spaces after
          % command names like \ldots made from \ + letters.
          %
          % Note how a `%' character causes TeX to ignore the
          % end of the input line, so these blank lines do not
          % start a new paragraph.
with the right spacing around the periods
requires a special  command.

\TeX\ interprets some common characters as commands, so you must type
special commands to generate them.  These characters include the
following:
%       \$ - arXiv do not like it...
        \& \% \# \{ and~\}.

In printing, text is emphasized by using an
       {\em italic\/}  % The \/ command produces the tiny extra space that
               % should be added between a slanted and a following
               % unslanted letter.
type style.

\begin{em}
   A long segment of text can also be emphasized in this way.  Text within
   such a segment given additional emphasis
      with\/ {\em Roman}
   type.  Italic type loses its ability to emphasize and become simply
   distracting when used excessively.
\end{em}

It is sometimes necessary to prevent \TeX\ from breaking a line where
it might otherwise do so.  This may be at a space, as between the
``Mr.'' and ``Jones'' in
       ``Mr.~Jones'',        % ~ produces an unbreakable interword space.
or within a word---especially when the word is a symbol like
       \mbox{\em itemnum\/}
that makes little sense when hyphenated across
       lines.

\TeX\ is good at typesetting mathematical formulas like
       \( x-3y = 7 \)
or
       \( a_{1} > x^{2n} / y^{2n} > x' \).
Remember that a letter like
       $x$        % $ ... $  and  \( ... \)  are equivalent
is a formula when it denotes a mathematical symbol, and should
be treated as one.

\section{Notes}
Footnotes\footnote{This is an example of a footnote.}
pose no problem\footnote{And another one}.

\section{Displayed text}

Text is displayed by indenting it from the left margin.
Quotations are commonly displayed.  There are short quotations
\begin{quote}
   This is a short a quotation.  It consists of a
   single paragraph of text.  There is no paragraph
   indentation.
\end{quote}
and longer ones.
\begin{quotation}
   This is a longer quotation.  It consists of two paragraphs
   of text.  The beginning of each paragraph is indicated
   by an extra indentation.

   This is the second paragraph of the quotation.  It is just
   as dull as the first paragraph.
\end{quotation}
Another frequently displayed structure is a list.
The following is an example of an {\em itemized} list, 
four levels deep.
\begin{itemize}
\item  This is the first item of an itemized list.  Each item
      in the list is marked with a ``tick.''  The document
      style determines what kind of tick mark is used.
\item  This is the second item of the list.  It contains another
      list nested inside it.  The three inner lists are an {\em itemized}
      list.
    \begin{itemize}
       \item This is the first item of an enumerated list that
            is nested within the itemized list.
          \item This is the second item of the inner list.  \LaTeX\
            allows you to nest lists deeper than you really should.
      \end{itemize}
      This is the rest of the second item of the outer list.  It
      is no more interesting than any other part of the item.
   \item  This is the third item of the list.
\end{itemize}

The following is an example of an {\em enumerated} list, four levels deep.
\begin{enumerate}
\item  This is the first item of an enumerated list.  Each item
      in the list is marked with a ``tick.''  The document
      style determines what kind of tick mark is used.
\item  This is the second item of the list.  It contains another
      list nested inside it.  The three inner lists are an {\em enumerated}
      list.
    \begin{enumerate}
       \item This is the first item of an enumerated list that
            is nested within the enumerated list.
          \item This is the second item of the inner list.  \LaTeX\
            allows you to nest lists deeper than you really should.
      \end{enumerate}
      This is the rest of the second item of the outer list.  It
      is no more interesting than any other part of the item.
   \item  This is the third item of the list.
\end{enumerate}

The following is an example of a {\em description} list.
\begin{description}
\item[Cow] Highly intelligent animal that can produce milk out of grass.
\item[Horse] Less intelligent animal renowned for its legs.
\item[Human being] Not so intelligent animal convinced it can think.
\end{description}

You can even display poetry.
\begin{verse}
   There is an environment for verse \\    % The \\ command separates lines
   Whose features some poets will curse.   % within a stanza.

               % One or more blank lines separate stanzas.

   For instead of making\\
   Them do {\em all\/} line breaking, \\
   It allows them to put too many words on a line when they'd
   rather be forced to be terse.
\end{verse}

Mathematical formulas may also be displayed.  A displayed formula is
one-line long:

   \[  x' + y^{2} = z_{i}^{2};\]

multiline formulas require special formatting
instructions.

Don't start a paragraph with a displayed equation, nor make
one a paragraph by itself.

Example of a theorem:

\begin{thm}
All conjectures are interesting, but some conjectures are more
interesting than others.
\end{thm}

\begin{proof}
Obvious.
\end{proof}

\section{Tables and figures}
Cross reference to labeled table: As you can see in Table~\ref{sphericcase} on
page~\pageref{sphericcase} and also in Table~\ref{parset} on page~\pageref{parset}.

\begin{table*}
\caption{The spherical case ($I_1=0$, $I_2=0$)}
\label{sphericcase}
\begin{tabular}{crrrrc}
\hline
Equil. \\
Points & \multicolumn{1}{c}{$x$} & \multicolumn{1}{c}{$y$} & \multicolumn{1}{c}{$z$} & \multicolumn{1}{c}{$C$} &
S \\
\hline
$~~L_1$ & $-$2.485252241 & 0.000000000 & 0.017100631 & 8.230711648 & U \\
$~~L_2$ &    0.000000000 & 0.000000000 & 3.068883732 & 0.000000000 & S \\
$~~L_3$ &    0.009869059 & 0.000000000 & 4.756386544 & $-$0.000057922 & U \\
$~~L_4$ &    0.210589855 & 0.000000000 & $-$0.007021459 & 9.440510897 & U \\
$~~L_5$ &    0.455926604 & 0.000000000 & $-$0.212446624 & 7.586126667 & U \\
$~~L_6$ &    0.667031314 & 0.000000000 & 0.529879957 & 3.497660052 & U \\
$~~L_7$ &    2.164386674 & 0.000000000 & $-$0.169308438 & 6.866562449 & U \\
$~~L_8$ &    0.560414471 & 0.421735658 & $-$0.093667445 & 9.241525367 & U \\
$~~L_9$ &    0.560414471 & $-$0.421735658 & $-$0.093667445 & 9.241525367 & U
\\
$~~L_{10}$ & 1.472523232 & 1.393484549 & $-$0.083801333 & 6.733436505 & U \\
$~~L_{11}$ & 1.472523232 & $-$1.393484549 & $-$0.083801333 & 6.733436505 & U
\\ \hline
\end{tabular}
\end{table*}

A major
point of difference lies in the value of the specific production rate $\pi$ for
large values of the specific growth rate $\mu$.
Already in the early publications \cite{r1,r2,r3}
it appeared that high glucose
concentrations in the production phase are well correlated with a
low penicillin yield (the
``glucose effect''). It has been confirmed recently
\cite{r1,r2,r3,r4}
that
high glucose concentrations inhibit the synthesis of the enzymes of the
penicillin pathway, but not the actual penicillin biosynthesis.
In other words, glucose represses (and not inhibits) the penicillin
biosynthesis.

These findings do not contradict the results of
\cite{r1}  and of \cite{r4} which were obtained for
continuous culture fermentations.
Because for high values of the specific
growth rate $\mu$ it is most likely (as shall be discussed below) that
maintenance metabolism occurs, it can be shown that
in steady state continuous culture conditions, and with $\mu$ described by a Monod kinetics
\begin{equation}
    C_{s}  =  K_{M} \frac{\mu/\mu_{x}}{1-\mu/\mu_{x}} \label{cs}
\end{equation}
Pirt \& Rhigelato determined $\pi$ for $\mu$ between
$0.023$ and $0.086$ h$^{-1}$.
They also reported a value $\mu_{x} \approx 0.095$
h$^{-1}$, so that for their experiments $\mu/\mu_{x}$ is in the range
of $0.24$ to $0.9$.
Substituting $K _M$ in equation (\ref{cs}) by
the value $K_{M}=1$ g/L as used by \cite{r1}, one finds
with the above equation $0.3 < C_{s} < 9$ g/L. This agrees with
the work of  \cite{r4}, who reported that penicillin biosynthesis
repression only occurs at glucose concentrations from $C_{s}=10$ g/L on.
The conclusion is that the glucose concentrations in the experiments of
Pirt \& Rhigelato probably were too low for glucose repression to be
detected. The experimental data published by Ryu \& Hospodka
are not detailed sufficiently to permit a similar analysis.

\begin{table}
\centering
\caption{Parameter sets used by Bajpai \& Reu\ss\ }\label{parset}
\begin{tabular}{lrll}
\hline
\multicolumn{2}{l}{\it parameter} & {\it Set 1} & {\it Set 2}\\
\hline
$\mu_{x}$           & [h$^{-1}$]  & 0.092       & 0.11          \\
$K_{x}$             & [g/g DM]     & 0.15        & 0.006         \\
$\mu_{p}$           & [g/g DM h]  & 0.005       & 0.004         \\
$K_{p}$             & [g/L]        & 0.0002      & 0.0001        \\
$K_{i}$             & [g/L]        & 0.1         & 0.1           \\
$Y_{x/s}$           & [g DM/g]     & 0.45        & 0.47          \\
$Y_{p/s}$           & [g/g]        & 0.9         & 1.2           \\
$k_{h}$             & [h$^{-1}$]  & 0.04        & 0.01          \\
$m_{s}$             & [g/g DM h]  & 0.014       & 0.029         \\
\hline
\end{tabular}
\end{table}

Bajpai \& Reu\ss\ decided to disregard the
differences between time constants for the two regulation mechanisms
(glucose repression or inhibition) because of the
relatively very long fermentation times, and therefore proposed a Haldane
expression for $\pi$.

It is interesting that simulations with the \cite{r4} model for the
initial conditions given by these authors indicate that, when the
remaining substrate is fed at a constant rate, a considerable and
unrealistic amount of penicillin is
produced when the glucose concentration is still very high \cite{r2,r3,r4}
Simulations with the Bajpai \& Reu\ss\ model correctly predict almost
no penicillin production in similar conditions.

\begin{figure} % figuur 1
\vspace{6pc}
\caption[]{Pathway of the penicillin G biosynthesis.}
\label{penG}
\end{figure}

Sample of cross-reference to figure.
Figure~\ref{penG} shows that is not easy to get something on paper.

\section{Headings}

\subsection{Subsection}
Carr--Goldstein based their model on balancing methods and
biochemical know\-ledge. The original model (1980) contained an equation for the
oxygen dynamics which has been omitted in a second paper
(1981). This simplified model shall be discussed here.

\subsubsection{Subsubsection}
Carr--Goldstein
based their model on balancing methods and
biochemical know\-ledge. The original model (1980) contained an equation for the
oxygen dynamics which has been omitted in a second paper
(1981). This simplified model shall be discussed here.

\section{Equations and the like}

Two equations:
\begin{equation}
    C_{s}  =  K_{M} \frac{\mu/\mu_{x}}{1-\mu/\mu_{x}} \label{ccs}
\end{equation}
and
\begin{equation}
    G = \frac{P_{\rm opt} - P_{\rm ref}}{P_{\rm ref}} \mbox{\ }100 \mbox{\ }(\%).
\end{equation}

Two equation arrays:

\begin{eqnarray}
  \frac{dS}{dt} & = & - \sigma X + s_{F} F\\
  \frac{dX}{dt} & = &   \mu    X\\
  \frac{dP}{dt} & = &   \pi    X - k_{h} P\\
  \frac{dV}{dt} & = &   F
\end{eqnarray}
and
\begin{eqnarray}
 \mu_{\rm substr} & = & \mu_{x} \frac{C_{s}}{K_{x}C_{x}+C_{s}}  \\
 \mu              & = & \mu_{\rm substr} - Y_{x/s}(1-H(C_{s}))(m_{s}+\pi /Y_{p/s}) \\
 \sigma           & = & \mu_{\rm substr}/Y_{x/s}+ H(C_{s}) (m_{s}+ \pi /Y_{p/s}).
\end{eqnarray}

\appendix

\section{Appendix section}\label{app}

We consider a sequence of queueing systems
indexed by $n$.  It is assumed that each system
is composed of $J$ stations, indexed by $1$
through $J$, and $K$ customer classes, indexed
by $1$ through $K$.  Each customer class
has a fixed route through the network of
stations.  Customers in class
$k$, $k=1,\ldots,K$, arrive to the
system according to a
renewal process, independently of the arrivals
of the other customer classes.  These customers
move through the network, never visiting a station
more than once, until they eventually exit
the system.

\subsection{Appendix subsection}

However, different customer classes may visit
stations in different orders; the system
is not necessarily ``feed-forward.''
We define the {\em path of class $k$ customers} in
as the sequence of servers
they encounter along their way through the network
and denote it by
\begin{equation}
\mathcal{P}=\bigl(j_{k,1},j_{k,2},\dots,j_{k,m(k)}\bigr). \label{path}
\end{equation}

Sample of cross-reference to the formula \ref{path} in Appendix \ref{app}.

\section*{Acknowledgements}
And this is an acknowledgements section with a heading that was produced by the
$\backslash$section* command. Thank you all for helping me writing this
\LaTeX\ sample file. See \ref{suppA} for the supplementary material example.

\begin{supplement}
\sname{Supplement A}\label{suppA}
\stitle{Title of the Supplement A}
\slink[url]{http://www.e-publications.org/ims/support/dowload/imsart-ims.zip}
\sdescription{Dum esset rex in
accubitu suo, nardus mea dedit odorem suavitatis. Quoniam confortavit
seras portarum tuarum, benedixit filiis tuis in te. Qui posuit fines tuos}
\end{supplement}

\begin{thebibliography}{9}

\bibitem{r1}
\textsc{Billingsley, P.} (1999). \textit{Convergence of
Probability Measures}, 2nd ed.
Wiley, New York.
\MR{1700749}

\bibitem{r2}
\textsc{Bourbaki, N.}  (1966). \textit{General Topology}  \textbf{1}.
Addison--Wesley, Reading, MA.

\bibitem{r3}
\textsc{Ethier, S. N.} and \textsc{Kurtz, T. G.} (1985).
\textit{Markov Processes: Characterization and Convergence}.
Wiley, New York.
\MR{838085}

\bibitem{r4}
\textsc{Prokhorov, Yu.} (1956).
Convergence of random processes and limit theorems in probability
theory. \textit{Theory  Probab.  Appl.}
\textbf{1} 157--214.
\MR{84896}

\end{thebibliography}

\end{document}

### 2018-04-11 analysis/April_Presentation.Rmd
adding a ton of stuff to the repo

--- 2018-04-05 April_Presentation.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE)
+```
+
+```{r, include = FALSE}
+
+#read in data
+#setwd("~/Carnegie-SEM/data")
+cc2015 <- read.csv("CC2015data.csv",header = TRUE)
+
+########2015################
+cc2015.full <- read.csv("CC2015data.csv", header = TRUE, as.is = TRUE)
+#updated file
+#cc2015.full <- read.csv("Updated2015.csv", header = TRUE)
+
+cc2015 <- cc2015.full[(cc2015.full$BASIC2015>14&cc2015.full$BASIC2015<18),]
+cc2015$BASIC2015 <- factor(cc2015$BASIC2015)
+
+#function for ranking the data
+minrank <- function(x){rank(x, ties.method = "min")}
+
+#dataset that we want to use
+cc2015Ps<-
+  na.omit(cc2015[,c("NAME","BASIC2010","BASIC2015","FACNUM","HUM_RSD",
+                    "OTHER_RSD","SOCSC_RSD","STEM_RSD","PDNFRSTAFF","S.ER.D","NONS.ER.D")])
+
+#calculate the ranked data
+cc2015.r <- data.frame(cc2015Ps[,1:3],sapply(cc2015Ps[,-c(1:3)],minrank))
+
+cc2015percap <- cc2015Ps[,c("PDNFRSTAFF","S.ER.D","NONS.ER.D")]/cc2015Ps$FACNUM
+
+colnames(cc2015percap) <- c("PDNRSTAFF_PC", "S.ER.D_PC", "NONS.ER.D_PC")
+#for Corrplot, nothing else
+
+cc2015percap.r<-data.frame(sapply(cc2015percap,minrank))
+cc2015_r <- cbind(cc2015.r, cc2015percap.r)
+#RUN THIS FOR CORRPLOT: (commented out otherwise)
+names(cc2015_r) <- c("Name","2010 Basic","2015 Basic","Faculty Size", "Hum PhD",
+                     "Other PhD","Soc. Sci PhD", "STEM PhD","Res. Staff", "STEM Exp", 
+                     "NS Exp", "Res. Staff PC", "STEM Exp PC  ", "NS Exp PC")
+
+cc2015_matrix2 <- as.matrix(cc2015_r[-c(1:3)])
+corrmatrix <- Hmisc::rcorr(cc2015_matrix2)
+
+par(mar = c(1,.8,.8,2))
+corrplot::corrplot(corrmatrix$r, order="hclust", type = "upper", method = 'number')
+text(-4,3, 'Correlation Plot', font = 2)
+text(-4,2,'of Manifest Variables', font = 2)
+rect(-7,1.3,-1,3.5)
+
+model4 <- '
+HUMANITIES=~HUM_RSD+OTHER_RSD+SOCSC_RSD+NONS.ER.D+FACNUM
+STEM=~STEM_RSD+PDNFRSTAFF+S.ER.D+FACNUM
+Aggregate=~HUMANITIES+STEM'
+
+model4 <- '
+non-STEM = ~ Hum PhD + Other PhD + Soc. Sci PhD + 
+STEM
+'
+
+library(lavaan)
+lavaan_sem_new <- lavaan::sem(model4, data=cc2015_r, std.lv=TRUE,
+                              orthogonal=FALSE, se="robust.huber.white")
+lavaan::summary(lavaan_sem_new, standardized=TRUE, fit.measures=TRUE)
+CCScores <- as.data.frame(lavaan::predict(lavaan_sem_new))
+rownames(CCScores) <- cc2015Ps$NAME
+
+#checks the standardized factor loadings
+inspect(lavaan_sem_new, what = 'std')$lambda
+
+#path diagram
+
+source('https://raw.githubusercontent.com/brandmaier/onyxR/master/tools/install.R')
+library(onyxR)
+onyx(lavaan_sem_new)
+
+library(beanplot)
+beanplot(CCScores$Aggregate,log="",col="yellow",method="jitter")
+
+library(mclust)
+mcres<-Mclust(CCScores$Aggregate)
+summary(mcres)
+
+Classifications <- as.data.frame(mcres[14:15])
+rownames(Classifications) <- cc2015Ps$NAME
+
+table(mcres$classification, cc2015Ps$BASIC2015) ## pretty good!!
+
+#Or more directly:
+dens<-densityMclust(CCScores$Aggregate)
+summary(dens)
+par(mfrow=c(1,2))
+plot(dens,what="diagnostic")
+
+#Or clustering the STEM and HUMANITIES scores (bivariate version)
+mcres2<-Mclust(CCScores[,1:2])
+
 ```
@@
 
+## What Data are used?
+Data used in the Carnegie Classifications are based on a snapshot from the Integrated Postsecondary Education Data System (IPEDS). The variables used in the classifications are:
+
++ STEM expenditures (in thousands of dollars)
++ Non-STEM expenditures (in thousands of dollars)
++ STEM PhD Counts
++ Humanities PhD Counts
++ Social Science PhD Counts
++ Nontenurable Research Staff size
++ Tenured/Tenure Track Faculty Headcount
+
 ## The Carnegie Methodology
 
-+ Rank Institutions
-+ Index Creation: PCA of aggregate and per-capita variables
-+ Plot the Indices (per-capita vs aggregate)
-+ Create groups (via line-drawing)
++ **Rank** Institutions
++ **Index Creation**: PCA of aggregate and per-capita variables
++ **Plot the Indices**:  (per-capita vs aggregate)
++ **Create groups**:  (via line-drawing)
+
+## Plot of the Carnegie Classifications
+```{r}
+
+```
 
@@
 The process used by the Carnegie Classifications illustrates several problems:
-+ Snapshot Data
-+ 
-+ 
-+
++ **Based on Snapshot Data**: Data are based on a single snapshot rather than averages during the five-year period.  
++ **Changing Loadings**: Loadings can change yearly based on variability in the data.
+This has the potential to change which variables are most important in determining the aggregate and per-capita indices.
++ **Dependence on Correlation**:  
++ **Group Determination**: The group determination is completely subjective. Lines are drawn after visual inspection of the plot ().
+
+\\
+This causes problems for schools that try to direct policy based on these classifications because the most important variables can be different from release to release based on variability in the data.
 
@@
 
-## STEM and Non-STEM Factors
+We can think of the Carnegie Classifications in a latent modeling framework using this path diagram:
+
+![Carnegie Model](carnegiepng.png)
+
+##Problems with the Carnegie Method for SEM:
+The variables used to measure the aggregate and per-capita latent variables are literally the same (with a slight per-capita transformation).
+The SEM cannot handle this level of correlation in the two latent factors; it **does not converge** and thus paramaters cannot be estimated.
+
+## STEM and Non-STEM Factors: An Alternative
 A more intuitive method would be to consider two latent factors:
@@
 
+![Correlation Plot of Observed Variables](corrplot_numbers.png)
+
+##Proposed Model: STEM and Non-STEM
+![Carnegie Model](onyx_final.png)
+
 ## Determining Group Membership
-The SEM model returns a single factor score for each university. These can be used as inputs to a
+The SEM model returns a single factor-of-factor score for each university.
+These can be used as inputs to a clustering algorithm to determine both the optimal number of clusters and the optimal cluster membership.
 
-## Group Membership
+__Potential Problems__:
+
++ Optimal Number of Clusters may be too large/small: We can fix this to a reasonable number if necessary (results here are fixed at 3). 
++ There are many different clustering methods to use (hierarchical clustering, mixture-model based methods, etc. )
+
+## Group Membership with Mixture Model:
+
+Using a mixture model approach, we can obtain a solution with reasonable clusters. Additionally, we can account for/illustrate uncertainty in classification for schools near the boundary.
+
+```{r plot_classifications}
+Classifications <- mcres$classification
+#creates a plot and colors by Carnegie Classification Colors  
+    ggplot(CCScores_r_cov_new) + geom_point(aes(x = STEM, y = HUM, color = factor(Classifications), shape = factor(symbols), size = factor(symbols)))+ 
+      ggtitle("Predicted vs Actual Classifications") + theme_bw() + coord_fixed(ratio = 1)+
+      theme_classic() + 
+      #theme(legend.position="right", legend.box = "vertical") + 
+      labs(color = "Classification")
+
+```
+
+## Shiny Applications: 
+We developed shiny applications to assess sensitivity of both the Carnegie Classifications and the proposed SEM-Classifications for any institution of your choosing.
+
+![Screenshot of the Application](app_screenshot.png)
+
+## Conclusions
+
+The SEM-based model allows for several benefits compared to the Carnegie Classifications:
+
++ Latent variables do not have to be orthogonal like PCA-based indices
++ Latent variable modeling makes more sense than dimension-reduction (especially since we only have 7 variables)
++ Single-factor scores allow for comparison on a single dimension rather than using two scores.
 
@@
 
-## Conclusions and
+Future work will focus on determining an optimal clustering strategy.
+The Carnegie Classifications themselves are changing, so if they change the variables that are used, we will investigate development of either a new latent trait or sensitivity of additional manifest variables to measure the STEM and non-STEM latent traits.
+
+##Questions:
+![]()

### 2018-04-11 SEM_app/SEM_app.R

@@ -8,8 +8,8 @@
 #
 
 #reads in the dataset needed
-library(dplyr);library(ggplot2);library(ggthemes)
-cc2015 <- filter(read.csv("C:/Users/paulh/Documents/Carnegie-SEM/data/CC2015data.csv",header = TRUE),BASIC2015 %in%c(15,16,17))
+library(dplyr);library(ggplot2);library(ggthemes);library(mclust)
+cc2015 <- filter(read.csv("CC2015data.csv",header = TRUE),BASIC2015 %in%c(15,16,17))
 
 names <- unique(cc2015$NAME)
 #gets the right package going
@@ -93,7 +93,7 @@ ui <- fluidPage(
 
 
 # GLOBAL CODE #######################################################
-cc2015 <- read.csv("C:/Users/paulh/Documents/Carnegie-SEM/data/CC2015data.csv",header = TRUE)
+cc2015 <- read.csv("CC2015data.csv",header = TRUE)
 
 #function for ranking the data
 minrank <- function(x){rank(x, ties.method = "min")}
@@ -188,13 +188,25 @@ COLOR <- rep(1,nrow(new_dat)); COLOR[a] <- 2
   ##Code to generate the plot and change the indices 
     CCScores_r_cov_new$symbols <- rep(0,length(CCScores_r_cov_new)) 
     CCScores_r_cov_new$symbols[a] <- 1
+  
+    ##Now we classify based on the scores
+    
+    mcres<-Mclust(CCScores_r_cov_new$Overall)
+    #summary(mcres)
+    
+    
+    Classifications <- mcres$classification
+    #rownames(Classifications) <- cc2015Ps$NAME
+    
   #creates a plot and colors by Carnegie Classification Colors  
-    ggplot(CCScores_r_cov_new) + geom_point(aes(x = STEM, y = HUM, color = factor(symbols), shape = factor(symbols), size = factor(symbols)))+ 
+    ggplot(CCScores_r_cov_new) + geom_point(aes(x = STEM, y = HUM, color = factor(Classifications), shape = factor(symbols), size = factor(symbols)))+ 
       ggtitle("Predicted vs Actual Classifications") + theme_bw() + coord_fixed(ratio = 1)+
-      theme_classic()
+      theme_classic() + guides(shape = FALSE) + guides(size = FALSE) + 
+      #theme(legend.position="right", legend.box = "vertical") + 
+      labs(color = "Classification") 
     
   
-  })
+})
 
   
   #render some test text

### 2018-04-11 SEM_app/app.R

@@ -8,8 +8,8 @@
 #
 
 #reads in the dataset needed
-library(dplyr)
-cc2015 <- filter(read.csv("C:/Users/paulh/Documents/Carnegie-SEM/data/CC2015data.csv",header = TRUE),BASIC2015 %in%c(15,16,17))
+library(dplyr);library(ggplot2);library(ggthemes);library(mclust)
+cc2015 <- filter(read.csv("CC2015data.csv",header = TRUE),BASIC2015 %in%c(15,16,17))
 
 names <- unique(cc2015$NAME)
 #gets the right package going
@@ -30,44 +30,40 @@ ui <- fluidPage(
     sidebarPanel(
       
       selectInput(inputId = "school", "School", choices = names, selected = NULL, multiple = FALSE,
-                  selectize = TRUE, width = NULL, size = NULL)
-      
-      , 
-      actionButton("update", "Change School")
-      ,
+                  selectize = TRUE, width = NULL, size = NULL), 
       
       hr(),
       
       sliderInput("sosc",
-                  "Number of Additional Social Science PhDs from 0:",
+                  "Number of Additional Social Science PhDs:",
                   min = 0,
                   max = 60,
                   value = 0)
       ,
       
       sliderInput("other",
-                  "Number of Additional Other PhDs from 9:",
+                  "Number of Additional Other PhDs:",
                   min = -9,
                   max = 50,
                   value = 0)
       ,
       sliderInput("stem",
-                  "Number of Additional STEM PhDs from 45:",
+                  "Number of Additional STEM PhDs:",
                   min = -45,
-                  max = 50,
+                  max = 5000,
                   step = 5,
                   value = 0)
       ,
       sliderInput("hum",
-                  "Number of Additional Humanities PhDs from 2:",
+                  "Number of Additional Humanities PhDs:",
                   min = -2,
                   max = 50,
                   value = 0)
       ,
       sliderInput("staff",
-                  "Additional Research Staff from 75:",
+                  "Additional Research Staff:",
                   min = -75,
-                  max = 2000,
+                  max = 20000,
[…]

### 2018-04-11 analysis/SEM_CleanCode.R

@@ -57,7 +57,7 @@ non-STEM = ~ Hum PhD + Other PhD + Soc. Sci PhD +
 STEM
 '
 
-
+library(lavaan)
 lavaan_sem_new <- lavaan::sem(model4, data=cc2015_r, std.lv=TRUE,
                               orthogonal=FALSE, se="robust.huber.white")
 lavaan::summary(lavaan_sem_new, standardized=TRUE, fit.measures=TRUE)
@@ -69,7 +69,7 @@ inspect(lavaan_sem_new, what = 'std')$lambda
 
 #path diagram
 
-source('https://raw.githubusercontent.com/brandmaier/onyxR/master/tools/install.R')
+#source('https://raw.githubusercontent.com/brandmaier/onyxR/master/tools/install.R')
 library(onyxR)
 onyx(lavaan_sem_new)
 

### 2019-05-10 AnswertoReviewer.Rmd
adding changes for paper

---
title: "Response to Review Comments"
author: "Paul Harmon"
date: "April 29, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pander)
library(semPlot)
```

## Introduction:

One of the points brought up by the reviewer is that the model is too sensitive to the size of the institutions. The reviewer notes the following in the feedback:

"Adopting the K&S variables cannot be imposed on these authors;  however, a parallel re-analysis using those 10 variables and a comparison with their current findings is HIGHLY DESIRABLE.  If the results are quite similar (as expected?), this
would remove an unimportant source of noise resulting from the small and variable number of PhD's produced
*each year* in the 3 boxes.  To be explicit, in point 4 above, produce a second HGHMM set of scores using the
K&S per capita variables.  The final two scores would be (1) the original (biased towards large schools andd
(2) a second (biased towards small schools via per capita."

We were unable to get the model to fit as a copy of the Carnegie version, but I interpret this comment as fitting the per-capita features into the SEM as we structured it.

## Model Results:

The results from our original model: 
```{r, out.width = '80%'}
library(dplyr);library(ggplot2);library(ggthemes);library(mclust);library(ggforce);library(shinyjs)
cc2015 <- filter(read.csv("data/CC2015data.csv",header = TRUE),BASIC2015 %in%c(15,16,17))
#dataset that we want to use
cc2015Ps<-
  na.omit(cc2015[,c("NAME","BASIC2010","BASIC2015","FACNUM","HUM_RSD","OTHER_RSD","SOCSC_RSD","STEM_RSD","PDNFRSTAFF","S.ER.D","NONS.ER.D")])
minrank <- function(x){rank(x, ties.method = "min")}
#calculate the ranked data
cc2015.r <- data.frame(cc2015Ps[,1:3],sapply(cc2015Ps[,-c(1:3)],minrank)) 
cc2015percap <- cc2015Ps[,c("PDNFRSTAFF","S.ER.D","NONS.ER.D")]/cc2015Ps$FACNUM
colnames(cc2015percap) <- c("PDNRSTAFF_PC", "S.ER.D_PC", "NONS.ER.D_PC")
cc2015percap.r<-data.frame(sapply(cc2015percap,minrank))

#sem using raw data
cc2015_new <- cbind(cc2015.r, cc2015percap)
#cc2015_new <- cc2015.r

model_alt <- '
#latent factors
STEM=~STEM_RSD+PDNFRSTAFF+S.ER.D + FACNUM
HUM=~HUM_RSD + OTHER_RSD + SOCSC_RSD + NONS.ER.D + FACNUM
#factor of factors
Overall=~STEM+HUM
'
lavaan_sem_r_alternate <- lavaan::sem(model_alt, data=cc2015_new, std.lv=TRUE, orthogonal=FALSE, se="robust.huber.white")

#predicts the scores
CCScores_r_cov <- as.data.frame(lavaan::predict(lavaan_sem_r_alternate))
CCScores_r_cov_new <- apply(CCScores_r_cov[,c(1,2)], 2, scale)

mcres<-Mclust(CCScores_r_cov$Overall)
#summary(mcres)
Classifications <- mcres$classification
    #rownames(Classifications) <- cc2015Ps$NAME
#creates a plot and colors by Carnegie Classification Colors  
ggplot(CCScores_r_cov) + geom_point(aes(x = STEM, y = HUM, color = factor(Classifications))) + 
ggtitle("Predicted vs Actual Classifications") + theme_bw() + coord_fixed(ratio = 1)+
theme_classic() + guides(shape = FALSE) + guides(size = FALSE) + 
labs(color = "Classification")+xlab("STEM") + ylab("Non-STEM")

Scores1 <- CCScores_r_cov
Class1 <- Classifications
```

```{r}
lavaan::summary(lavaan_sem_r_alternate, fit.measures=TRUE)
```

## Alternate Model

The model with Per-capita included looks a little different. A path diagram is given below.

```{r, out.width = '100%'}
model_alt2 <- '
#latent factors
STEM=~STEM_RSD+PDNFRSTAFF+S.ER.D + FACNUM + S.ER.D_PC + PDNRSTAFF_PC
HUM=~HUM_RSD + OTHER_RSD + SOCSC_RSD + NONS.ER.D + FACNUM + NONS.ER.D_PC
#factor of factors
Overall=~STEM+HUM
'

lavaan_sem_r_alternate <- lavaan::sem(model_alt2, data=cc2015_new, std.lv=TRUE, orthogonal=FALSE, se="robust.huber.white")

semPaths(lavaan_sem_r_alternate)

#predicts the scores
CCScores_r_cov <- as.data.frame(lavaan::predict(lavaan_sem_r_alternate))
CCScores_r_cov_new <- apply(CCScores_r_cov[,c(1,2)], 2, scale)

mcres<-Mclust(CCScores_r_cov$Overall)
#summary(mcres)
Classifications <- mcres$classification
    #rownames(Classifications) <- cc2015Ps$NAME
#creates a plot and colors by Carnegie Classification Colors  
ggplot(CCScores_r_cov) + geom_point(aes(x = -STEM, y = HUM, color = factor(Classifications))) + 
ggtitle("Predicted vs Actual Classifications") + theme_bw() + coord_fixed(ratio = 1)+
theme_classic() + guides(shape = FALSE) + guides(size = FALSE) + 
labs(color = "Classification")+xlab("-1*STEM") + ylab("Non-STEM")

Scores2 <- CCScores_r_cov
Scores2$Name <- cc2015_new$NAME
Class2 <- Classifications
```

The summary of the model is here:

```{r}
lavaan::summary(lavaan_sem_r_alternate, fit.measures=TRUE)
```

## Results

These are very preliminary results, but the shape hasn't changed drastically. A couple of institutions get pulled away from the rest of the cluster - the bottom one on the stem scale is interesting. Including per-capita features does not seem to cause problems in the SEM model, as the model converges.

However, the sign on the STEM term has flipped - loadings are now negative, and I had to reverse the order of the STEM factor to get the plot to point in the direction we expected to see. (This does not have an effect on the groupings but is interesting nonetheless).  Looking at the estimated coefficients for the loadings and their associated p-values, we see that the evidence in favor of an effect of the humanities latent factor is moderate at best; nearly all the p-values for the model with per-capita features indicate diminished strength of evidence.

Looking at some of the individual school classifications, we see that Cal Tech remains in the middle-size category and that .

```{r}
x <- tibble(Scores2$Name, Scores1$Overall, Scores2$Overall, Class1, Class2)
names(x) <- c("Name","Score1","Score2", "M1Class", "M2Class")
#x$DifferenceSq <- (x$Score1 - x$Score2)^2
x$AbsDiff <- abs(x$Score1 - x$Score2)

#biggest difference schools
arrange(x, desc(AbsDiff)) %>% head(15) %>% pander()

```

### 2019-05-10 AlternateApp/app.R

@@ -1,0 +1,398 @@
+#
+# Paul Harmon
+# README: The Shiny App created here is written by Paul Harmon. Its intent is to assess the sensitivity of the 
+# Carnegie Classifications to small changes in the underlying variables used to calculate each index. 
+#
+# Note that the functions and data must be read in prior to running this code. The easiest way to do this right now is 
+# probably is to just run all of the code in the R-Code for Carnegie Stuff.R file. We might source it in later .
+#
+
+#reads in the dataset needed
+library(dplyr);library(ggplot2);library(ggthemes);library(mclust);library(ggforce);library(shinyjs)
+cc2015 <- filter(read.csv("CC2015data.csv",header = TRUE),BASIC2015 %in%c(15,16,17))
+
+names <- unique(cc2015$NAME)
+#gets the right package going
+library(shiny); library(shinythemes)
+
+
+###UI #######################################
+# Define UI for application that allows you to pick a college and see how it would change
+ui <- fluidPage(
+  #shiny theme
+  theme = shinytheme("superhero"),
+  
+  # Application title
+  titlePanel("Sensitivity of the SEM Scale Classifications"),
+  
+  # Sidebar with a slider input for number of bins 
+  sidebarLayout(
+    sidebarPanel(
+      
+      selectInput(inputId = "school", "School", choices = names, selected = NULL, multiple = FALSE,
+                  selectize = TRUE), 
+      useShinyjs(),
+      hr(),
+      actionButton("resetAll", "Reset all",style = "background-color: gray;"),
+      hr(),
+      div( id = "form",
+           sliderInput("sosc",
+                       "Number of Additional Social Science PhDs:",
+                       min = 0,
+                       max = 60,
+                       value = 0)
+           ,
+           
+           sliderInput("other",
+                       "Number of Additional Other PhDs:",
+                       min = -9,
+                       max = 50,
+                       value = 0)
+           ,
+           sliderInput("stem",
[…]

### 2019-05-10 CarnegieSEM_paul.R

@@ -1,6 +1,6 @@
 #read in data
 setwd("~/Carnegie-SEM/data")
-cc2015 <- read.csv("CC2015data.csv",header = TRUE)
+cc2015 <- read.csv("data/CC2015data.csv",header = TRUE)
 
 ########2015################
 cc2015.full <- read.csv("CC2015data.csv", header = TRUE, as.is = TRUE)
@@ -227,10 +227,55 @@ lavaan::summary(lavaan_sem_r_alternate, fit.measures=TRUE)
 #path diagram
 semPaths(lavaan_sem_r_alternate)
 
-
 predict_alt <- lavaan::predict(lavaan_sem_r_alternate)
 plot(-predict_alt[,1],-predict_alt[,2], col = cc2015_r$BASIC2015, pch = 11)
 plot(density(-predict_alt[,3]))
+
+
+
+### Version with Per-capita variables included
+model_alt2 <- '
+#latent factors
+STEM=~STEM_RSD+PDNFRSTAFF+S.ER.D + FACNUM + S.ER.D_PC + PDNRSTAFF_PC
+HUM=~HUM_RSD + OTHER_RSD + SOCSC_RSD + NONS.ER.D + FACNUM + NONS.ER.D + PDNRSTAFF_PC
+#factor of factors
+Overall=~STEM+HUM
+
+
+'
+lavaan_sem_r_alternate2 <- lavaan::sem(model_alt2, data=cc2015_r, std.lv=TRUE, orthogonal=FALSE, se="robust.huber.white")
+lavaan::summary(lavaan_sem_r_alternate2, fit.measures=TRUE)
+
+
+##predicts the scores
+CCScores_r_cov_new <- as.data.frame(lavaan::predict(lavaan_sem_r_alternate2))
+range_scores_new <- max(CCScores_r_cov_new$Overall) - min(CCScores_r_cov_new$Overall)
+CCScores_r_cov_new$rate_2015 <- ifelse(CCScores_r_cov_new$Overall < min(CCScores_r_cov_new$Overall)+((1/3)*range_scores), 'A', ifelse(CCScores_r_cov$Overall > max(CCScores_r_cov$Overall)-((1/3)*range_scores), 'C', 'B'))
+
+##Code to generate the plot and change the indices 
+CCScores_r_cov_new$symbols <- rep(0,length(CCScores_r_cov_new)) 
+CCScores_r_cov_new$symbols[a] <- 1
+
[…]

### 2019-05-10 SEM_app/alt_app.R

@@ -1,0 +1,419 @@
+#
+# Paul Harmon
+# README: The Shiny App created here is written by Paul Harmon. Its intent is to assess the sensitivity of the 
+# Carnegie Classifications to small changes in the underlying variables used to calculate each index. 
+#
+# Note that the functions and data must be read in prior to running this code. The easiest way to do this right now is 
+# probably is to just run all of the code in the R-Code for Carnegie Stuff.R file. We might source it in later .
+#
+
+#reads in the dataset needed
+library(dplyr);library(ggplot2);library(ggthemes);library(mclust);library(ggforce);library(shinyjs)
+cc2015 <- filter(read.csv("CC2015data.csv",header = TRUE),BASIC2015 %in%c(15,16,17))
+
+names <- unique(cc2015$NAME)
+#gets the right package going
+library(shiny); library(shinythemes)
+
+
+###UI #######################################
+# Define UI for application that allows you to pick a college and see how it would change
+ui <- fluidPage(
+  #shiny theme
+  theme = shinytheme("superhero"),
+  
+  # Application title
+  titlePanel("Sensitivity of the SEM Scale Classifications"),
+  
+  # Sidebar with a slider input for number of bins 
+  sidebarLayout(
+    sidebarPanel(
+      
+      selectInput(inputId = "school", "School", choices = names, selected = NULL, multiple = FALSE,
+                  selectize = TRUE), 
+      useShinyjs(),
+      hr(),
+      actionButton("resetAll", "Reset all",style = "background-color: gray;"),
+      hr(),
+      div( id = "form",
+           sliderInput("sosc",
+                       "Number of Additional Social Science PhDs:",
+                       min = 0,
+                       max = 60,
+                       value = 0)
+           ,
+           
+           sliderInput("other",
+                       "Number of Additional Other PhDs:",
+                       min = -9,
+                       max = 50,
+                       value = 0)
+           ,
+           sliderInput("stem",
[…]
